---
title: "AD_att1"
author: "Natalie Chong"
date: "5/12/2020"
output: html_document
---
# Step 1: Set parameters; simulate to equilibrium
```{r}
Hcol <- 'hotpink'
Rcol <- 'peru'
Mcol <- 'seagreen3'
Ncol <- 'dodgerblue'
D <- 0.5 # Dilution Rate (Outflow)
R_0 <- 25 # Inflow Concentration (Nitrogen)
l <- 0.05 # fungal mortality
s <- 0.05 # senescence coefficient
c <- 0.7 # host's C:N Ratio
u_res <- 0.3 #Fungus M uptake rate
u_n <- 0 #Fungus N uptake rate
#f <- 0.5/2 + 0.5*(u_m*M/(u_m*M + u_n*N)) # fidelity of plant allocation to Fungi M
#1- f 
#a <- 0.5/2 +0.5*(u_n/(u_m + u_n))
x <- u_res/6 #cost of mutualism of Fungi M
y <- u_n/6 #cost of mutualsim of Fungi N
b <- 0.3 #symbiont's intrinsic growth rate
C_a <- 0.2 #Allocation Carbon
C_c <- 0.3 #Construction Carbon 
v <- 0.3  #Conversion efficiency, Host carbon to more symbionts
```

```{r}
tset <- seq(from=0, to= 300, length.out = 10000)
H.simu1 <- NaN*tset; H.simu1[1] <- 1
M.simu1 <- NaN*tset; M.simu1[1] <- 1
R.simu1 <- NaN*tset; R.simu1[1] <- 10
N.simu1 <- NaN*tset; N.simu1[1] <- 0


#*M *N *H
for(i in 2:length(tset)){
    dt <- tset[i] - tset[i-1] 
    H <- H.simu1[i-1] 
    M <- M.simu1[i-1]
    R <- R.simu1[i-1]
    N <- N.simu1[i-1]
    f <- 0.5/2 + 0.5*(u_res*M/(u_res*M + u_n*N))
   
    
    dR <- (D*(R_0 - R) - u_res*M*R - u_n*N*R + (s*H)/c)*dt
    dH <- (c*u_res*R*M + c*u_n*R*N - (s*H) - ((u_res*C_a) + C_c)*M*H - (C_c + (u_n)*C_a)*N*H )*dt
    dM <- (b*(1-x)*v*(C_c + (u_res*C_a))*H*M - l*M)*dt
    dN <- (b*(1-y)*v*(C_c + (u_n*C_a))*H*N - l*N)*dt
    
    H.simu1[i] <- H + dH
    M.simu1[i] <- M + dM
    N.simu1[i] <- N + dN
    R.simu1[i] <- R + dR
    
}

#legend(x = 75, y = 10.5 , legend = c(), lwd=2, col = c())
plot(x = tset, y = H.simu1, col = Hcol,type = 'l',ylim = c(0, 20),xlab = 'Time', ylab = 'Species biomass/Resource Abundance', lwd=2,las=1) 
lines(x = tset, y = R.simu1,type='l',las=1,lwd=2,ylab='Resource',xlab='Time',col=Rcol)
lines(x = tset, y = M.simu1, col = Mcol, lwd=2) 
lines(x = tset, y = N.simu1, col = Ncol, lwd=2) 
legend(x = 150, y = 20, legend = c('Host','Mutualist M', 'Mutant N', 'Resource'), lwd=2, col = c(Hcol,Mcol,Ncol,Rcol))
#tail(H.simu1); tail( M.simu1); tail(R.simu1)

```

# Step 2 : Pick mutant trait value
```{r}
#u_res <- 0.3
#u_mut <- max(rnorm (1, u_res, sd = 0.1), 0)
u_mut <- 0.286825
```

# Step 3: Split M* into resident and mutant pools
```{r}
m_i <- 0.99*M.simu1[length(tset)]
n_i <- 0.01*M.simu1[length(tset)]

```

# Step 4: Simulate dynamics from new initial conditions
```{r}
R0 <- R.simu1[length(tset)]
H0 <- H.simu1[length(tset)]
#M0 <- m_i
#N0 <- n_i
```

#Step 5: Who's the winner?
```{r}
mutset1 <- seq(from=0, to= 10000, .1)
H.simu2 <- NaN*mutset1; H.simu2[1] <- H0
M.simu2 <- NaN*mutset1; M.simu2[1] <- m_i
R.simu2 <- NaN*mutset1; R.simu2[1] <- R0
N.simu2 <- NaN*mutset1; N.simu2[1] <- n_i


#*M *N *H
for(i in 2:length(mutset1)){
    dt <- mutset1[i] - mutset1[i-1] 
    H <- H.simu2[i-1] 
    M <- M.simu2[i-1]
    R <- R.simu2[i-1]
    N <- N.simu2[i-1]
   # f <- 0.5/2 + 0.5*(u_res*M/(u_res*M + u_mut*N))
    
  
    
    dR <- (D*(R_0 - R) - u_res*M*R - u_mut*N*R + (s*H)/c)*dt
    dH <- (c*u_res*R*M + c*u_mut*R*N - (s*H) - ((u_res*C_a) + C_c)*M*H - (C_c + (u_mut)*C_a)*N*H )*dt
    dM <- (b*(1-x)*v*(C_c + (u_res*C_a))*H*M - l*M)*dt
    dN <- (b*(1-y)*v*(C_c + (u_mut*C_a))*H*N - l*N)*dt
    
    H.simu2[i] <- H + dH
    M.simu2[i] <- M + dM
    N.simu2[i] <- N + dN
    R.simu2[i] <- R + dR
    
    
}

if(any(is.na(M.simu2))||(M.simu2[length(mutset1)] - M.simu2[length(mutset1) - 1])/M.simu2[length(mutset1)-1] >  0.000001) { warning("Oh noes! Something is still changing at end of simulation!!") } # || stop circuit sign, can only do for things that are not vectors. 
if(any(is.na(N.simu2))||(N.simu2[length(mutset1)] - N.simu2[length(mutset1) - 1])/N.simu2[length(mutset1)-1] >  0.000001) { warning("Oh noes! Something is still changing at end of simulation!!") }
N.simu2[length(mutset1)]; M.simu2[length(mutset1)]
N.simu2[length(mutset1)] / (N.simu2[length(mutset1)] + M.simu2[length(mutset1)])
N.simu2[length(mutset1) -1 ] / (N.simu2[length(mutset1) -1] + M.simu2[length(mutset1) -1 ])
(N.simu2[length(mutset1)] / (N.simu2[length(mutset1)] + M.simu2[length(mutset1)])) - (N.simu2[length(mutset1) -1 ] / (N.simu2[length(mutset1) -1] + M.simu2[length(mutset1) -1 ]))
#output
#legend(x = 75, y = 10.5 , legend = c(), lwd=2, col = c())
plot(x = mutset1, y = H.simu2, col = Hcol,type = 'l',ylim = c(0, 20),xlab = 'Time', ylab = 'Species biomass/Resource Abundance', lwd=2,las=1) 
lines(x = mutset1, y = R.simu2,type='l',las=1,lwd=2,ylab='Resource',xlab='Time',col=Rcol)
lines(x = mutset1, y = M.simu2, col = Mcol, lwd=2) 
lines(x = mutset1, y = N.simu2, col = Ncol, lwd=2) 
legend(x = 300, y = 20, legend = c('Host','Mutualist M', 'Mutant N', 'Resource'), lwd=2, col = c(Hcol,Mcol,Ncol,Rcol))
#tail(H.simu2); tail( M.simu2); tail(R.simu2)
```
*Mutant won, spreads in population. u_res = u_mut, m_i = 0.99 Nstar *

#THE BETTER WAY: Double For Loop  
```{r}
mutset1.6 <- rep(NaN,200) #still need to run 1000 rounds of mutations.
mutset1.6[1] <- 0.7 # initial uptake rate. 

#initial conditions for double loop. After system equilibriates stores eq values of R, H, M & N vector. 
tset <- seq(from=0, to= 300, length.out = 10000)
H.simu1 <- NaN*tset; H.simu1[1] <- 1
M.simu1 <- NaN*tset; M.simu1[1] <- 1
R.simu1 <- NaN*tset; R.simu1[1] <- 10
N.simu1 <- NaN*tset; N.simu1[1] <- 0


for(i in 2:length(tset)){
    dt <- tset[i] - tset[i-1] 
    H <- H.simu1[i-1] 
    M <- M.simu1[i-1]
    R <- R.simu1[i-1]
    N <- N.simu1[i-1]
   # f <- 0.5/2 + 0.5*(u_res*M/(u_res*M + u_n*N))
   
    
    dR <- (D*(R_0 - R) - u_res*M*R - u_n*N*R + (s*H)/c)*dt
    dH <- (c*u_res*R*M + c*u_n*R*N - (s*H) - ((u_res*C_a) + C_c)*M*H - (C_c + (u_n)*C_a)*N*H )*dt
    dM <- (b*(1-x)*v*(C_c + (u_res*C_a))*H*M - l*M)*dt
    dN <- (b*(1-y)*v*(C_c + (u_n*C_a))*H*N - l*N)*dt
    
    H.simu1[i] <- H + dH
    M.simu1[i] <- M + dM
    N.simu1[i] <- N + dN
    R.simu1[i] <- R + dR
    
}
H0 <- H.simu1[length(tset)]
R0 <- R.simu1[length(tset)]
M_i <- M.simu1[length(tset)]
N_i <- N.simu1[length(tset)]

H0 ; R0 ; M_i ; N_i
 H <- H0
 M <- M_i
 R <- R0
 N <- N_i
  
dt <- 0.01

for(i in 2:length(mutset1.6)){ #mutset1.6: records every individual who won, 's uptake rate. 
  delta <- 0.99 # mutant percentage in the population  
  numberofreps <- 0 
  u_mut <- max(rnorm (1, mutset1.6[i-1], sd = 0.05), 0)
  N <- .05*M
  M <- .95*M
  u_res <- mutset1.6[i-1] 
  
 #normally outside of for loop stuff goes here, before while.
 #simulate initial dynamics. Before mutation runs. (Steps 3-4) 
  
  while(numberofreps < 1000000 && (delta < 0.955 && delta > 0.045)){ # && means and, if previous is not true then won't run second. Other criteria: mutant declines, if delta is greater than 95.5% or less than .45%. 
    #while loop Simulates dynamics. 
    numberofreps <- numberofreps + 1; 
    
    dR <- (D*(R_0 - R) - u_res*M*R - u_mut*N*R + (s*H)/c)*dt
    dH <- (c*u_res*R*M + c*u_mut*R*N - (s*H) - ((u_res*C_a) + C_c)*M*H - (C_c + (u_mut)*C_a)*N*H )*dt
    dM <- (b*(1-(u_res/6))*v*(C_c + (u_res*C_a))*H*M - l*M)*dt
    dN <- (b*(1-(u_mut/6))*v*(C_c + (u_mut*C_a))*H*N - l*N)*dt
    
    H <- H + dH
    M <- M + dM
    N<- N + dN
    R<- R + dR
    delta <- N / (N+M)
    if(is.na(delta)){print("delta is not a number")}
if(is.na(numberofreps)){print("#ofreps is not a number")}
    #1st:maybe step size is too large - dt. Check with is.na function. 
    # 2nd: have possibility of coexistance. 
  
  }
 
  # Code below records who won. If M reaches 95% take it still as the new resident, and if N reaches 95% replaces M as the new resident. If neither is true print warning and break. 
 
  #print("delta=")
  print(delta)
  
if(delta < 0.955 && delta > 0.045){print("delta is intermediate")
  print(u_mut)
  print(u_res)
  break}
    if(delta >= 0.955){mutset1.6[i] <- u_mut} 
    if(delta <= 0.045){mutset1.6[i] <- u_res}
 
}
 print("mutset1.6=")
  print(mutset1.6)
  
  plot(x = 1:length(mutset1.6), y = mutset1.6, xlab = 'Rounds of mutations', ylab = 'Uptake Rates',lwd=2,las=1)
  
  #run with 1000 rounds of mutations.
  #figure out where we get coexistance. compare different pairs of mutations and residents looking at combinations of values. 
  #evolution preceeds in different directions...maybe everytime we start a new generation, pop size shrinks briefly. potential non-eq thing occuring.

```



# Comparing a combination of u values, via a matrix.
```{r}
D <- 0.5 # Dilution Rate (Outflow)
R_0 <- 25 # Inflow Concentration (Nitrogen)
l <- 0.05 # fungal mortality
s <- 0.05 # senescence coefficient
c <- 0.7 # host's C:N Ratio
u_res <- 0.3 #Fungus M uptake rate
u_n <- 0 #Fungus N uptake rate
#f <- 0.5/2 + 0.5*(u_m*M/(u_m*M + u_n*N)) # fidelity of plant allocation to Fungi M
b <- 0.3 #symbiont's intrinsic growth rate
C_a <- 0.2 #Allocation Carbon
C_c <- 0.3 #Construction Carbon 
v <- 0.3  #Conversion efficiency, Host carbon to more symbionts
```


```{r}
mutset1.7 <- matrix(NaN,nrow = 20, ncol = 20, dimnames = list(seq(1/20, 1, 1/20), seq(1/20, 1, 1/20))) #name rows to be u_m ; cols to be u_n. made a matrix thingie yay
mutset1.7[1] <- 0.7

dt <- 0.01

for(i in 1:nrow(mutset1.7)){ #mutset1.6: records every individual who won. nrow here is analogous to "length" command.
u_m <-  as.numeric(rownames(mutset1.7)[i]) 
   
#**    
tset <- seq(from=0, to= 300, length.out = 10000)
H.simu1 <- NaN*tset; H.simu1[1] <- 1
M.simu1 <- NaN*tset; M.simu1[1] <- 1
R.simu1 <- NaN*tset; R.simu1[1] <- 10
#N.simu1 <- NaN*tset; N.simu1[1] <- 0


for(k in 2:length(tset)){
    dt <- tset[k] - tset[k-1] 
    H <- H.simu1[k-1] 
    M <- M.simu1[k-1]
    R <- R.simu1[k-1]
  #  N <- N.simu1[k-1]
   # f <- 0.5/2 + 0.5*(u_res*M/(u_res*M + u_n*N))
   
    
    dR <- (D*(R_0 - R) - u_m*M*R+ (s*H)/c)*dt
    dH <- (c*u_m*R*M  - (s*H) - ((u_m*C_a) + C_c)*M*H  )*dt
    dM <- (b*(1-(u_m/6))*v*(C_c + (u_m*C_a))*H*M - l*M)*dt
   # dN <- (b*(1-(u_mut/6))*v*(C_c + (u_mut*C_a))*H*N - l*N)*dt
    
    H.simu1[k] <- H + dH
    M.simu1[k] <- M + dM
    #N.simu1[k] <- N + dN
    R.simu1[k] <- R + dR
    
}
H0 <- H.simu1[length(tset)]
R0 <- R.simu1[length(tset)]
M_i <- M.simu1[length(tset)]
#N_i <- N.simu1[length(tset)]

#H0 ; R0 ; M_i ; N_i
 H <- H0
 M <- M_i
 R <- R0
 #N <- N_i
 dt <- 0.01
      #added equilibrated resident population size. starting from **
 for(j in 1: ncol(mutset1.7)){
    u_n <- as.numeric(colnames(mutset1.7)[j]) # do whole while loop, initialize u_n and u_m to actual numbers, store delta in the matrix. 
   
    
   
  delta <- 0.99 # mutant percentage in the population  
  numberofreps <- 0 
  #normally outside of for loop stuff goes here before while.
 #simulates dynamics initial.
  N <- .01*M_i #change according to what the resident equilibrates to..
  M <- .99*M_i
  H <- H0
  R <- R0
  #print(u_m); print(u_n); print(R); print(H); print(dt)
 # mutset1.7[[i, j]] <- delta #records delta, where delta is intermediate coexistance occured. 
  
  #mark down how host was before simu. 
  
  while(numberofreps < 1000000 && (delta < 0.995 && delta > 0.005)){ # && means and, if previous is not true then won't run second. Other criteria: mutant declines, if delta is greater than 99.5% or less than .5%. Simulates dynamics. 
    numberofreps <- numberofreps + 1; 
    
    dR <- (D*(R_0 - R) - u_m*M*R - u_n*N*R + (s*H)/c)*dt
    dH <- (c*u_m*R*M + c*u_n*R*N - (s*H) - ((u_m*C_a) + C_c)*M*H - (C_c + (u_n)*C_a)*N*H )*dt
    dM <- (b*(1-(u_m/6))*v*(C_c + (u_m*C_a))*H*M - l*M)*dt
    dN <- (b*(1-(u_n/6))*v*(C_c + (u_n*C_a))*H*N - l*N)*dt
    
    H <- H + dH
    M <- M + dM
    N<- N + dN
    R<- R + dR
    delta <- N / (N+M)
    if(is.na(delta)){print("delta is not a number"); print(N); print (M)}
if(is.na(numberofreps)){print("#ofreps is not a number")} #1st:maybe step size is too large - dt. Check with is.na function. 
    # 2nd: have possibility of coexistance. 
  
  }
  if(delta < 0.995 && delta > 0.005){print("delta is intermediate")
 #print(u_m)
  #print(u_n)
 }
   mutset1.7[[i,j]] <- delta  
   
   # mark down how host was after simu. 
   if (delta >= 0.995){  mutset1.7[[i,j]] <- 1  }
   if(delta <= 0.005){mutset1.7[[i,j]] <- 0  }
   } 
  # records who won. If M reaches 99% take it still as the new resident, and if N reaches 99% replaces M as the new resident. If neither is true print warning and break. 
 
  
}
 print("mutset1.7=")
  print(mutset1.7)
  print(round(mutset1.7, 3))
  
#directions:  
  # more mutualistic things invade.look at parameters to ask why.  
  # how does host feels about partners that have u_m = 1 Depending on whether you want to look at Host before and after the simulation, you could either do *, or do
       # Part 2: host is making taking over slow down? do it the old fashion way using eg. 0.3(col) and 0.25 (row).
  #potential coexistance, is it true:- run for longer to find out.
  #maybe try to bring back fidelity factor? [/] -problem: MUTANT CAN'T INVADE...
  #google pairwise invasibility plots. 
# install.packages('plot.matrix')
  library('plot.matrix')
  Mutant_percentage<-mutset1.7

  plot(Mutant_percentage, border= NA, fmt.cell='%.3f', fmt.key ="%.3f", breaks = c(-0.1,0.011,.99,1),xlab= "u_n", ylab = "u_m", col = c('white','grey','black') ) 

```



# Step 6: Repeat from step 2 with u_mut as new u_res!
```{r}
u_res2 <- u_mut
#u_mut2 <- max(rnorm (1, u_res2, sd = 0.1), 0)
u_mut2 <- 0.2736905
```


```{r}
m_i2 <- 0.99*N.simu2[length(mutset1)]
n_i2 <- 0.01*M.simu2[length(mutset1)]
```

```{r}
R0 <- R.simu2[length(mutset1)]
H0 <- H.simu2[length(mutset1)]
#M0 <- m_i
#N0 <- n_i
```

```{r}
mutset1.1 <- seq(from=0, to= 10000, .1)
H.simu3 <- NaN*mutset1.1; H.simu3[1] <- H0
M.simu3 <- NaN*mutset1.1; M.simu3[1] <- m_i2
R.simu3 <- NaN*mutset1.1; R.simu3[1] <- R0
N.simu3 <- NaN*mutset1.1; N.simu3[1] <- n_i2


#*M *N *H
for(i in 2:length(mutset1.1)){
    dt <- mutset1.1[i] - mutset1.1[i-1] 
    H <- H.simu3[i-1] 
    M <- M.simu3[i-1]
    R <- R.simu3[i-1]
    N <- N.simu3[i-1]
    f <- 0.5/2 + 0.5*(u_res2*M/(u_res2*M + u_mut2*N))
   
    
    dR <- (D*(R_0 - R) - u_res2*M*R - u_mut2*N*R + (s*H)/c)*dt
    dH <- (c*u_res2*R*M + c*u_mut2*R*N - (s*H) - ((u_res2*C_a) + C_c)*M*H - (C_c + (u_mut2)*C_a)*N*H )*dt
    dM <- (b*(1-x)*v*(C_c + (u_res2*C_a))*H*M - l*M)*dt
    dN <- (b*(1-y)*v*(C_c + (u_mut2*C_a))*H*N - l*N)*dt
    
    H.simu3[i] <- H + dH
    M.simu3[i] <- M + dM
    N.simu3[i] <- N + dN
    R.simu3[i] <- R + dR
    
}

#legend(x = 75, y = 10.5 , legend = c(), lwd=2, col = c())
plot(x = mutset1.1, y = H.simu3, col = Hcol,type = 'l',ylim = c(0, 20),xlab = 'Time', ylab = 'Species biomass/Resource Abundance', lwd=2,las=1) 
lines(x = mutset1.1, y = R.simu3,type='l',las=1,lwd=2,ylab='Resource',xlab='Time',col=Rcol)
lines(x = mutset1.1, y = M.simu3, col = Mcol, lwd=2) 
lines(x = mutset1.1, y = N.simu3, col = Ncol, lwd=2) 
legend(x = 300, y = 20, legend = c('Host','Mutualist M', 'Mutant N', 'Resource'), lwd=2, col = c(Hcol,Mcol,Ncol,Rcol))
tail(H.simu3); tail(M.simu3); tail(R.simu3)
# 3800- 3850
```

*Mutant won again, rises later with slightly lower u.*

# Step 7: umut3; mutset1.2; simu4
```{r}
u_res3 <- u_mut2
#u_mut3 <- max(rnorm (1, u_res3, sd = 0.1), 0)
u_mut3 <- 0.3455529
```


```{r}
m_i3 <- 0.99*N.simu3[length(mutset1.1)]
n_i3 <- 0.01*M.simu3[length(mutset1.1)]
```

```{r}
R0 <- R.simu3[length(mutset1.1)]
H0 <- H.simu3[length(mutset1.1)]
#M0 <- m_i3
#N0 <- n_i3
```

```{r}
mutset1.2 <- seq(from=0, to= 3000, length.out = 10000)
H.simu4 <- NaN*mutset1.2; H.simu4[1] <- H0
M.simu4 <- NaN*mutset1.2; M.simu4[1] <- m_i3
R.simu4 <- NaN*mutset1.2; R.simu4[1] <- R0
N.simu4 <- NaN*mutset1.2; N.simu4[1] <- n_i3


#*M *N *H
for(i in 2:length(mutset1.2)){
    dt <- mutset1.2[i] - mutset1.2[i-1] 
    H <- H.simu4[i-1] 
    M <- M.simu4[i-1]
    R <- R.simu4[i-1]
    N <- N.simu4[i-1]
    f <- 0.5/2 + 0.5*(u_res3*M/(u_res3*M + u_mut3*N))
   
    
    dR <- (D*(R_0 - R) - u_res3*M*R - u_mut3*N*R + (s*H)/c)*dt
    dH <- (c*u_res3*R*M + c*u_mut3*R*N - (s*H) - ((u_res3*C_a) + C_c)*M*H - (C_c + (u_mut3)*C_a)*N*H )*dt
    dM <- (b*(1-x)*v*(C_c + (u_res3*C_a))*H*M - l*M)*dt
    dN <- (b*(1-y)*v*(C_c + (u_mut3*C_a))*H*N - l*N)*dt
    
    H.simu4[i] <- H + dH
    M.simu4[i] <- M + dM
    N.simu4[i] <- N + dN
    R.simu4[i] <- R + dR
    
}

#legend(x = 75, y = 10.5 , legend = c(), lwd=2, col = c())
plot(x = mutset1.2, y = H.simu4, col = Hcol,type = 'l',ylim = c(0, 20),xlab = 'Time', ylab = 'Species biomass/Resource Abundance', lwd=2,las=1) 
lines(x = mutset1.2, y = R.simu4,type='l',las=1,lwd=2,ylab='Resource',xlab='Time',col=Rcol)
lines(x = mutset1.2, y = M.simu4, col = Mcol, lwd=2) 
lines(x = mutset1.2, y = N.simu4, col = Ncol, lwd=2) 
legend(x = 300, y = 20, legend = c('Host','Mutualist M', 'Mutant N', 'Resource'), lwd=2, col = c(Hcol,Mcol,Ncol,Rcol))
tail(H.simu4); tail(M.simu4); tail(R.simu4)
```

*mutant invades*

# Step 8: u_res4; umut4; m_i4; mutset1.3; simu5
```{r}
u_res4 <- u_mut3 #0.3455529
#u_mut4 <- max(rnorm (1, u_res4, sd = 0.1), 0)
u_mut4 <- 0.2511468
```


```{r}
m_i4 <- 0.99*N.simu4[length(mutset1.2)]
n_i4 <- 0.01*M.simu4[length(mutset1.2)]
```

```{r}
R0 <- R.simu4[length(mutset1.2)]
H0 <- H.simu4[length(mutset1.2)]
#M0 <- m_i4
#N0 <- n_i4
```

```{r}
mutset1.3 <- seq(from=0, to= 10000, .1)
H.simu5 <- NaN*mutset1.3; H.simu5[1] <- H0
M.simu5 <- NaN*mutset1.3; M.simu5[1] <- m_i4
R.simu5 <- NaN*mutset1.3; R.simu5[1] <- R0
N.simu5 <- NaN*mutset1.3; N.simu5[1] <- n_i4


#*M *N *H
for(i in 2:length(mutset1.3)){
    dt <- mutset1.3[i] - mutset1.3[i-1] 
    H <- H.simu5[i-1] 
    M <- M.simu5[i-1]
    R <- R.simu5[i-1]
    N <- N.simu5[i-1]
    f <- 0.5/2 + 0.5*(u_res4*M/(u_res4*M + u_mut4*N))
   
    
    dR <- (D*(R_0 - R) - u_res4*M*R - u_mut4*N*R + (s*H)/c)*dt
    dH <- (c*u_res4*R*M + c*u_mut4*R*N - (s*H) - ((u_res4*C_a) + C_c)*M*H - (C_c + (u_mut4)*C_a)*N*H )*dt
    dM <- (b*(1-x)*v*(C_c + (u_res4*C_a))*H*M - l*M)*dt
    dN <- (b*(1-y)*v*(C_c + (u_mut4*C_a))*H*N - l*N)*dt
    
    H.simu5[i] <- H + dH
    M.simu5[i] <- M + dM
    N.simu5[i] <- N + dN
    R.simu5[i] <- R + dR
    
}

#legend(x = 75, y = 10.5 , legend = c(), lwd=2, col = c())
plot(x = mutset1.3, y = H.simu5, col = Hcol,type = 'l',ylim = c(0, 20),xlab = 'Time', ylab = 'Species biomass/Resource Abundance', lwd=2,las=1) 
lines(x = mutset1.3, y = R.simu5,type='l',las=1,lwd=2,ylab='Resource',xlab='Time',col=Rcol)
lines(x = mutset1.3, y = M.simu5, col = Mcol, lwd=2) 
lines(x = mutset1.3, y = N.simu5, col = Ncol, lwd=2) 
legend(x = 300, y = 10, legend = c('Host','Mutualist M', 'Mutant N', 'Resource'), lwd=2, col = c(Hcol,Mcol,Ncol,Rcol))
tail(H.simu5); tail(M.simu5); tail(R.simu5)
```
*Mutualist wins, N fails to invade, u_res remains, Mi = 0.99 x Mstar*

# Step 9: u_res5; umut5; m_i5; mutset1.4; simu6; RES WON!
```{r}
u_res5 <- u_res4 #0.3455529
#u_mut5 <- max(rnorm (1, u_res5, sd = 0.1), 0)
u_mut5 <- 0.3665069
```


```{r}
m_i5 <- 0.99*M.simu5[length(mutset1.3)]
n_i5 <- 0.01*N.simu5[length(mutset1.3)]
```

```{r}
R0 <- R.simu5[length(mutset1.3)]
H0 <- H.simu5[length(mutset1.3)]
#M0 <- m_i5
#N0 <- n_i5
```

```{r}
mutset1.4 <- seq(from=0, to= 3200, .1)
H.simu6 <- NaN*mutset1.4; H.simu6[1] <- H0
M.simu6 <- NaN*mutset1.4; M.simu6[1] <- m_i5
R.simu6 <- NaN*mutset1.4; R.simu6[1] <- R0
N.simu6 <- NaN*mutset1.4; N.simu6[1] <- n_i5


#*M *N *H
for(i in 2:length(mutset1.4)){
    dt <- mutset1.4[i] - mutset1.4[i-1] 
    H <- H.simu6[i-1] 
    M <- M.simu6[i-1]
    R <- R.simu6[i-1]
    N <- N.simu6[i-1]
    f <- 0.5/2 + 0.5*(u_res5*M/(u_res5*M + u_mut5*N))
   
    
    dR <- (D*(R_0 - R) - u_res5*M*R - u_mut5*N*R + (s*H)/c)*dt
    dH <- (c*u_res5*R*M + c*u_mut5*R*N - (s*H) - ((u_res5*C_a) + C_c)*M*H - (C_c + (u_mut5)*C_a)*N*H )*dt
    dM <- (b*(1-x)*v*(C_c + (u_res5*C_a))*H*M - l*M)*dt
    dN <- (b*(1-y)*v*(C_c + (u_mut5*C_a))*H*N - l*N)*dt
    
    H.simu6[i] <- H + dH
    M.simu6[i] <- M + dM
    N.simu6[i] <- N + dN
    R.simu6[i] <- R + dR
    
}

#legend(x = 75, y = 10.5 , legend = c(), lwd=2, col = c())
plot(x = mutset1.4, y = H.simu6, col = Hcol,type = 'l',ylim = c(0, 20),xlab = 'Time', ylab = 'Species biomass/Resource Abundance', lwd=2,las=1) 
lines(x = mutset1.4, y = R.simu6,type='l',las=1,lwd=2,ylab='Resource',xlab='Time',col=Rcol)
lines(x = mutset1.4, y = M.simu6, col = Mcol, lwd=2) 
lines(x = mutset1.4, y = N.simu6, col = Ncol, lwd=2) 
legend(x = 300, y = 10, legend = c('Host','Mutualist M', 'Mutant N', 'Resource'), lwd=2, col = c(Hcol,Mcol,Ncol,Rcol))
tail(H.simu6); tail(M.simu6); tail(N.simu6); tail(R.simu6)
```
*Mutualist wins, N fails to invade, u_res remains, Mi = 0.99 x Mstar*

# Step 10: u_res6; umut6; m_i6; mutset1.5; simu7; RES WON!
```{r}
u_res6 <- u_res5 
#u_mut6 <- max(rnorm (1, u_res6, sd = 0.1), 0)
u_mut6 <- 0.4285827
```


```{r}
m_i6 <- 0.99*M.simu6[length(mutset1.4)]
n_i6 <- 0.01*N.simu6[length(mutset1.4)]
```

```{r}
R0 <- R.simu6[length(mutset1.4)]
H0 <- H.simu6[length(mutset1.4)]
#M0 <- m_i5
#N0 <- n_i5
```

```{r}
mutset1.5 <- seq(from=0, to= 2500, .1)
H.simu7 <- NaN*mutset1.5; H.simu7[1] <- H0
M.simu7 <- NaN*mutset1.5; M.simu7[1] <- m_i6
R.simu7 <- NaN*mutset1.5; R.simu7[1] <- R0
N.simu7 <- NaN*mutset1.5; N.simu7[1] <- n_i6


#*M *N *H
for(i in 2:length(mutset1.5)){
    dt <- mutset1.5[i] - mutset1.5[i-1] 
    H <- H.simu7[i-1] 
    M <- M.simu7[i-1]
    R <- R.simu7[i-1]
    N <- N.simu7[i-1]
    f <- 0.5/2 + 0.5*(u_res6*M/(u_res6*M + u_mut6*N))
   
    
    dR <- (D*(R_0 - R) - u_res6*M*R - u_mut6*N*R + (s*H)/c)*dt
    dH <- (c*u_res6*R*M + c*u_mut6*R*N - (s*H) - ((u_res6*C_a) + C_c)*M*H - (C_c + (u_mut6)*C_a)*N*H )*dt
    dM <- (b*(1-x)*v*(C_c + (u_res6*C_a))*H*M - l*M)*dt
    dN <- (b*(1-y)*v*(C_c + (u_mut6*C_a))*H*N - l*N)*dt
    
    H.simu7[i] <- H + dH
    M.simu7[i] <- M + dM
    N.simu7[i] <- N + dN
    R.simu7[i] <- R + dR
    
}

#legend(x = 75, y = 10.5 , legend = c(), lwd=2, col = c())
plot(x = mutset1.5, y = H.simu7, col = Hcol,type = 'l',ylim = c(0, 20),xlab = 'Time', ylab = 'Species biomass/Resource Abundance', lwd=2,las=1) 
lines(x = mutset1.5, y = R.simu7,type='l',las=1,lwd=2,ylab='Resource',xlab='Time',col=Rcol)
lines(x = mutset1.5, y = M.simu7, col = Mcol, lwd=2) 
lines(x = mutset1.5, y = N.simu7, col = Ncol, lwd=2) 
legend(x = 300, y = 10, legend = c('Host','Mutualist M', 'Mutant N', 'Resource'), lwd=2, col = c(Hcol,Mcol,Ncol,Rcol))
tail(H.simu7); tail(M.simu7); tail(N.simu7); tail(R.simu7)
```