---
title: "Bifurcation_Diagrams_2.0"
author: "Natalie Chong"
date: "8/9/2020"
output: html_document
---
# This Markdown records my attempt to break down the Host equation to figure out how each part changes with uptake rate!
```{r}
D <- 0.5 # Dilution Rate (Outflow)
R_0 <- 25 # Inflow Concentration (Nitrogen)
l <- 0.05 # fungal mortality
s <- 0.05 # senescence coefficient
c <- 0.7 # host's C:N Ratio
z <- 0.3 #cost of being a mutualist per unit of uptake rate* 
C_a <- 0.3 #Allocation Carbon
C_c <- 0.2 #Construction Carbon 
v <- 0.1  #Conversion efficiency, Host carbon to more symbionts
a <- 1.747721 # Resource's half-saturation constant.**This is k in equation!**
l_x <- 0.2 # loss back to R pool per unit of nutrient, let resident and mutant to have the same loss
l_y <- 0.2
g <- 0.8 #Tree's per capita groth rate

fun <- function(u_m,R){(((u_m)*R)/((a)+R))}
x <- function(u_m, R, H){(u_m*R)/(l_x + g*H)}
```

# First I shall be recording R*, H* and M*.
# Here's M* v.s. u_m
```{r}
uset <- seq(1/20, 1, 1/20)
Mset <- NaN*uset

for(i in 1:length(uset)){ #for every placeholder i from 1 to the entire length of uset.
  u_m <- as.numeric(uset[i]) # set u_m as a numeric number.
tset <- seq(from=0, to= 300, length.out = 10000) #setting initial conditions, setting a time sequence that starts from 0 to 300, sliced in 10000 pieces. 
H.simu1 <- NaN*tset; H.simu1[1] <- 1 #fill variables with NaNs, to the length of how long tset is. Also set intial conditions.
M.simu1 <- NaN*tset; M.simu1[1] <- 1
R.simu1 <- NaN*tset; R.simu1[1] <- 10

for(k in 2:length(tset)){
    dt <- tset[k] - tset[k-1] 
    H <- H.simu1[k-1] 
    M <- M.simu1[k-1]
    R <- R.simu1[k-1]
  
    
    dR <- (D*(R_0 - R) + s*H/c - u_m*R*M + l_x*M*x(u_m, R,H))*dt
    dH <- (c*g*x(u_m, R, H)*H*M  - (s*H) - ((fun(u_m,R)*C_a) + C_c)*M*H  )*dt #host can't exist without already being in the system!
    dM <- (v*(1-(u_m*z))*(C_c + (fun(u_m,R)*C_a))*H*M - l*M)*dt
  
    
    H.simu1[k] <- H + dH
    M.simu1[k] <- M + dM
    R.simu1[k] <- R + dR
    
}
Mset[i] <- M.simu1[length(tset)]

}

plot(uset, Mset, type='l', lwd=2, xlab = "Uptake Rate, u_m", ylab = "Resident Abundance at equilibrium, M*", col = 'blue')
```

# Plotting R* as a function of uptake rate
```{r}
uset <- seq(1/20, 1, 1/20)
Rset <- NaN*uset

for(i in 1:length(uset)){
  u_m <- as.numeric(uset[i])
tset <- seq(from=0, to= 300, length.out = 10000)
H.simu1 <- NaN*tset; H.simu1[1] <- 1
M.simu1 <- NaN*tset; M.simu1[1] <- 1
R.simu1 <- NaN*tset; R.simu1[1] <- 10

for(k in 2:length(tset)){
    dt <- tset[k] - tset[k-1] 
    H <- H.simu1[k-1] 
    M <- M.simu1[k-1]
    R <- R.simu1[k-1]
  
    
    dR <- (D*(R_0 - R) + s*H/c - u_m*R*M + l_x*M*x(u_m, R,H))*dt
    dH <- (c*g*x(u_m, R, H)*H*M  - (s*H) - ((fun(u_m,R)*C_a) + C_c)*M*H  )*dt #added H term in the positive portion of the equation, host can't exist without already being in the system!
    dM <- (v*(1-(u_m*z))*(C_c + (fun(u_m,R)*C_a))*H*M - l*M)*dt
  
    
    H.simu1[k] <- H + dH
    M.simu1[k] <- M + dM
    R.simu1[k] <- R + dR
    
}
Rset[i] <- R.simu1[length(tset)]

}

plot(uset, Rset, type='l', col = Rcol, lwd=2, xlab = "Uptake Rate, u_m", ylab = "Host Abundance at equilibrium, R*")
```

#Plotting H* as a function of uptake rate
```{r}
uset <- seq(1/20, 1, 1/20)
Hset <- NaN*uset

for(i in 1:length(uset)){
  u_m <- as.numeric(uset[i])
tset <- seq(from=0, to= 300, length.out = 10000)
H.simu1 <- NaN*tset; H.simu1[1] <- 1
M.simu1 <- NaN*tset; M.simu1[1] <- 1
R.simu1 <- NaN*tset; R.simu1[1] <- 10

for(k in 2:length(tset)){
    dt <- tset[k] - tset[k-1] 
    H <- H.simu1[k-1] 
    M <- M.simu1[k-1]
    R <- R.simu1[k-1]
  
    
    dR <- (D*(R_0 - R) + s*H/c - u_m*R*M + l_x*M*x(u_m, R,H))*dt
    dH <- ( c*g*x(u_m, R, H)*H*M  - (s*H) - ((fun(u_m,R)*C_a) + C_c)*M*H)*dt #host can't exist without already being in the system!
    dM <- (v*(1-(u_m*z))*(C_c + (fun(u_m,R)*C_a))*H*M - l*M)*dt
  
    
    H.simu1[k] <- H + dH
    M.simu1[k] <- M + dM
    R.simu1[k] <- R + dR
    
}
Hset[i] <- H.simu1[length(tset)]

}

plot(uset, Hset, type='l', lwd=2, xlab = "Uptake Rate, u_m", ylab = "Host Abundance at equilibrium, H*", col = 'green')
```

# Now I have H*, R*, and M* for each of the 20 u_m values!
# Next step is to calculate each element within our dH/dt equation, the host growth term, the senescence term, and the fungal payments term.
$$
\begin{align}
\frac{dH}{dt} &= cgH \cdot \frac{u_mRM}{l_x + gH} - s H - ( f_m C_a + C_c ) M H \\ 
\newline
\end{align}

$$
# For the Host Growth term.
# ps. Initial values for each term was calculated by hand.
```{r}
Gset <- NaN*Hset #this is where I'm about to hold my values. Basically it's 20 slots of NaNs. 
tset1 <- seq(0, 19/20, by = 1/20)
G.simu1 <- NaN*Hset; G.simu1[1] <- 0 # Outer loop: Initial value for G is 0 (Because when u_m is zero the growth term is zero!) Also 20 slots of NaNs.
for(i in 1:length(uset)){ # for every item in uset for the entire length of uset.
 u_m <- as.numeric(uset[i]) # set the value for u_m within the equation as every numerical number present in uset (?). Numbers range from 0 to 19/20 by 1/20.
    
      R <- Rset[i]
      H <- Hset[i]
      M <- Mset[i]
      

  
      dG <- (c*g*x(u_m, R, H)*H*M) # Just looking at the change in our growth term for now!
  
      G.simu1[i] <- dG

 }
 Gset <- G.simu1


head(G.simu1) ; tail(G.simu1); Gset # Check values recorded in Gset

```

#Okay the math for our growth term didn't quite checkout(R's values v.s. my calculator's), double check calculator cuz senescence seems fine!
#Let's move on to our senescence term to see if that'll work
```{r}
Sset <- NaN*Hset
tset1 <- seq(0,19/20, by = 1/20)
S.simu1 <- NaN*Hset; S.simu1[1] <- 2.411478*0.05

for(i in 1:length(uset)){
  u_m <- as.numeric(uset[i]) #For every numerical number within uset, put it as u_m at each timestep.
    R <- Rset[i]
    H <- Hset[i]
    M <- Mset[i]
  
      dS <- (s*H) # looking at our senescence term only.
  
      S.simu1[i] <- dS

 }
 Sset <- S.simu1

head(Sset) ; tail(Sset)
```

#Cool the code for senescence checks out! Edit Growth term to match :) 
# A match and the outcome was the same as our previous code. Hmm. Maybe it IS my math!
# Next lets generate and save our Host to fungal payments term.
```{r}
Pset <- NaN*Hset
P.simu1 <- NaN*Hset; P.simu1[1] <- 0
for(i in 1:length(uset)){
  u_m <- as.numeric(uset[i]) #For every numerical number within uset, put it as u_m at each timestep.
    R <- Rset[i]
    H <- Hset[i]
    M <- Mset[i]
    
  
      dP <- ((fun(u_m,R)*C_a) + C_c)*M*H
  
      P.simu1[i] <- dP

 }
 Pset <- P.simu1


head(Pset) ; tail(Pset) ; Pset
```

# Lets plot their respective bifurcation diagrams then!
# For our Host Growth term
```{r}
plot(uset, Gset, type='l', lwd=2, xlab = "Uptake Rate, u_m", ylab = "Host Growth term at equilibrium, G*")
```

# For Host to fungal payments
```{r}
plot(uset, Pset, type='l', lwd = 2, xlab  = "Uptake Rate, u_m", ylab = "Host to Fungal payments term at equilibrium, P*")
```

# For Senescence.
```{r}
plot(uset, Sset, type='l', lwd = 2, xlab  = "Uptake Rate, u_m", ylab = "Senescence term at equilibrium, S*")
```

# Yay! You've generated graphs! *Congrats*
#Combination
```{r}
plot(uset, Gset-Sset-Pset, type='l', lwd = 2, xlab  = "Uptake Rate, u_m", ylim = c(0,5), ylab = "Senescence term at equilibrium, S*") #YOU CAN DO THIS
lines(uset, Hset, lwd = 2, lty = 2)
```

# Plotting Fidelity
```{r}
fset <- NaN*Hset
f.simu1 <- NaN*Hset; f.simu1[1] <- 0
for(i in 1:length(uset)){
  u_m <- as.numeric(uset[i]) #For every numerical number within uset, put it as u_m at each timestep.
    R <- Rset[i]
    H <- Hset[i]
    M <- Mset[i]
    
  
      df <- fun(u_m,R)
  
      f.simu1[i] <- df

 }
 fset <- f.simu1


head(fset) ; tail(fset) ; fset
plot(uset, fset, type='l', lwd = 2, xlab  = "Uptake Rate, u_m", ylab = "Fidelity*")
```

```{r}
(fset*C_a + C_c)*Hset*Mset
```

```{r}
(c*g*Hset*uset*Rset*Mset)/(l_x +g*Hset)
```

