---
title: "Model_4.0"
author: "Natalie Chong"
date: "7/31/2020"
output: html_document
---

# Fungus Model version 4.0: Added short-term nutrient pool between resident symbiont and Host - X, to ensure that uptake and growth terms are carefully coupled! Changed cost of mutualism to z*(u). Also eliminated b - Fungal intrinsic growth rate term, and used v to represent per capita fungal growth instead.

#Used separation of timescales, and assumed that X exists in a much shorter timeline than other organisms in the system. So that in comparison, dX/dt = 0

# Before invasion (no mutant(N) population yet..)
$$
\begin{align}
\frac{dR}{dt} &= D ( R_0 - R ) + \frac{1}{c} s H - u_mRM + l_x \cdot \frac{u_mRM}{l_x + gH} \\ 
\newline
\frac{dH}{dt} &= cgH \cdot \frac{u_mRM}{l_x + gH} - s H - ( f_m C_a + C_c ) M H \\ 
\newline
\frac{dM}{dt} &= v ( 1 - zu_m )  ( f_m C_a + C_c ) M H - l M\\ 
\newline
\frac{dX}{dt} &= \frac{u_mR}{k_m + R} \cdot M - l_xx - \frac{u_mRM}{l_x + gH} = 0 \\
\newline
f_m &= \frac{u_mR}{k_m + R}
\end{align}

$$

# After adding mutant.
$$
\begin{align}

\newline
\frac{dR}{dt} &= D ( R_0 - R ) + \frac{1}{c} s H - u_mMR  - u_nNR + l_xM \cdot \frac{u_mR}{l_x + gH} + l_yN \cdot  \frac{u_nR}{l_y + gH}\\ 
\newline
\frac{dH}{dt} &= cgH \cdot \frac{u_mRM}{l_x + gH} + cgH \cdot \frac{u_nRN}{l_y + gH} - s H - ( f_m C_a + C_c ) M H - ( f_n C_a + C_c ) N H \\ 
\newline
\frac{dM}{dt} &= v ( 1 - zu_m )  ( f_m C_a + C_c ) M H - l M\\ 
\newline
\frac{dY}{dt} &= \frac{u_nR}{k_n + R} \cdot M - l_yy - \frac{u_nRM}{l_y + gH} = 0
\newline
\frac{dN}{dt} &= v ( 1 - zu_n )  ( f_n C_a + C_c ) N H - l N
\newline
f_n &= \frac{u_nR}{k_n + R} \\ f_m &= \frac{u_mR}{k_m + R} \\ 
\end{align}
$$
# Lets see what this does! Setting parameters.
*star symbols indicate descriptions that could be worded better*
# second to the last plot: z= 0.2, v=0.1
# last plot: z= 0.3, v= 0.05 +z-v, host was still unhappy
#now z=0.3, v=0.1 
```{r}
D <- 0.5 # Dilution Rate (Outflow)
R_0 <- 25 # Inflow Concentration (Nitrogen)
l <- 0.05 # fungal mortality
s <- 0.05 # senescence coefficient
c <- 0.7 # host's C:N Ratio what will changing you do.. what is the ACTUAL C:N ratio?
z <- 0.3 #cost of being a mutualist per unit of uptake rate* 
C_a <- 0.3 #Allocation Carbon
C_c <- 0.2 #Construction Carbon 
v <- 0.1  #Conversion efficiency, Host carbon to more symbionts
a <- 1.747721 # Resource's half-saturation constant.**This is k in equation!**
l_x <- 0.2 # loss back to R pool per unit of nutrient, let resident and mutant to have the same loss
l_y <- 0.2
g <- 0.8 #Tree's per capita groth rate



fun <- function(u_m,R){(((u_m)*R)/((a)+R))}
x <- function(u_m, R, H){(u_m*R)/(l_x + g*H)}

```

#Create PIP
```{r}
mutset4.0 <- matrix(NaN,nrow = 20, ncol = 20, dimnames = list(seq(1/20, 1, 1/20), seq(1/20, 1, 1/20))) 
dt <- 0.01

for(i in 1:nrow(mutset4.0)){ 
u_m <-  as.numeric(rownames(mutset4.0)[i]) 
   
#Setting initial conditions (letting ecological dynamics play out)   
tset <- seq(from=0, to= 200, length.out = 10000)
H.simu1 <- NaN*tset; H.simu1[1] <- 1
M.simu1 <- NaN*tset; M.simu1[1] <- 1
R.simu1 <- NaN*tset; R.simu1[1] <- 10


for(k in 2:length(tset)){
    dt <- tset[k] - tset[k-1] 
    H <- H.simu1[k-1] 
    M <- M.simu1[k-1]
    R <- R.simu1[k-1]
  
    
    dR <- (D*(R_0 - R) + s*H/c - u_m*R*M + l_x*M*x(u_m, R,H))*dt
    dH <- (c*g*x(u_m, R, H)*H*M  - (s*H) - ((fun(u_m,R)*C_a) + C_c)*M*H  )*dt #host can't exist without already being in the system!
    dM <- (v*(1-(u_m*z))*(C_c + (fun(u_m,R)*C_a))*H*M - l*M)*dt
  
    H.simu1[k] <- H + dH
    M.simu1[k] <- M + dM
    R.simu1[k] <- R + dR
    
}
# Save end values(@equilibrium) to holding vector.
H0 <- H.simu1[length(tset)]
R0 <- R.simu1[length(tset)]
M_i <- M.simu1[length(tset)]

 H <- H0
 M <- M_i
 R <- R0

 dt <- 0.01
    
 for(j in 1: ncol(mutset4.0)){
    u_n <- as.numeric(colnames(mutset4.0)[j]) 
   
  delta <- 0.99
  numberofreps <- 0 

  # insert 1% of mutant population into the system
  N <- .01*M_i 
  M <- .99*M_i
  H <- H0
  R <- R0
 
  
  while(numberofreps < 1000000  && (delta < 0.995 && delta > 0.005)){
    numberofreps <- numberofreps + 1; 
    
     dR <- (D*(R_0 - R) + s*H/c - u_m*R*M + l_x*M*x(u_m, R, H) - u_n*R*N + l_y*N*x(u_n, R, H))*dt
    dH <- (c*g*x(u_m, R, H)*H*M + c*g*x(u_n, R, H)*H*N - (s*H) - ((fun(u_m,R)*C_a) + C_c)*M*H - ((fun(u_n,R)*C_a) + C_c)*N*H)*dt #host can't exist without already being in the system!
    dM <- (v*(1-(u_m*z))*(C_c + (fun(u_m,R)*C_a))*H*M - l*M)*dt
    dN <- (v*(1-(u_n*z))*(C_c + (fun(u_n,R)*C_a))*H*N - l*N)*dt
    
    H <- H + dH
    M <- M + dM
    N<- N + dN
    R<- R + dR
    delta <- N / (N+M)
    if(is.na(delta)){print("delta is not a number"); print(N); print (M)}
if(is.na(numberofreps)){print("#ofreps is not a number")} 
  }
  
   mutset4.0[[i,j]] <- delta  
   
   
   if (delta >= 0.995){  mutset4.0[[i,j]] <- 1  }
   if(delta <= 0.005){mutset4.0[[i,j]] <- 0  }
   } 
 
}
 
  print(round(mutset4.0, 3))
  
   library('plot.matrix')
  Mutant_percentage4<-mutset4.0
 par(mar = c(4,4,4,4))
  plot(Mutant_percentage4, border= NA, fmt.key ="%.2f", breaks = c(-0.1,0.012,1),xlab= "Mutant Uptake Rate, u_n", ylab = "Resident Uptake Rate, u_m", col = c('white','black') ) 
```

# Record Average resident uptake rate at each mutation round.
```{r}
mutset4.1 <-  matrix(NaN,nrow = 20, ncol = 20, dimnames = list(seq(1/20, 1, 1/20), seq(1/20, 1, 1/20))) 
dt <- 0.01

for(i in 1:nrow(mutset4.1)){ 
u_m <-  as.numeric(rownames(mutset4.1)[i]) 
   
#Setting initial conditions (letting ecological dynamics play out) 
tset <- seq(from=0, to= 300, length.out = 10000)
H.simu1 <- NaN*tset; H.simu1[1] <- 1
M.simu1 <- NaN*tset; M.simu1[1] <- 1
R.simu1 <- NaN*tset; R.simu1[1] <- 10


for(k in 2:length(tset)){
    dt <- tset[k] - tset[k-1] 
    H <- H.simu1[k-1] 
    M <- M.simu1[k-1]
    R <- R.simu1[k-1]
  
    
    dR <- (D*(R_0 - R) + s*H/c - u_m*R*M + l_x*M*x(u_m, R,H))*dt
    dH <- (c*g*x(u_m, R, H)*H*M  - (s*H) - ((fun(u_m,R)*C_a) + C_c)*M*H  )*dt #host can't exist without already being in the system!
    dM <- (v*(1-(u_m*z))*(C_c + (fun(u_m,R)*C_a))*H*M - l*M)*dt
  
    
    H.simu1[k] <- H + dH
    M.simu1[k] <- M + dM
    R.simu1[k] <- R + dR
    
}
H0 <- H.simu1[length(tset)]
R0 <- R.simu1[length(tset)]
M_i <- M.simu1[length(tset)]



 H <- H0
 M <- M_i
 R <- R0
 dt <- 0.01
     
 for(j in 1: ncol(mutset4.1)){
    u_n <- as.numeric(colnames(mutset4.1)[j])  
   
    
   delta <- 0.99  
  numberofreps <- 0 
  
  N <- .01*M_i 
  M <- .99*M_i
  H <- H0
  R <- R0
  
  
  while(numberofreps < 1000000 && (delta < 0.995 && delta > 0.005)){ # && means and, if previous is not true then won't run second. Other criteria: mutant declines, if delta is greater than 99.5% or less than .5%. Simulates dynamics. 
    numberofreps <- numberofreps + 1; 
    
   dR <- (D*(R_0 - R) + s*H/c - u_m*R*M + l_x*M*x(u_m, R, H) - u_n*R*N + l_y*N*x(u_n, R, H))*dt
    dH <- (c*g*x(u_m, R, H)*H*M + c*g*x(u_n, R, H)*H*N - (s*H) - ((fun(u_m,R)*C_a) + C_c)*M*H - ((fun(u_n,R)*C_a) + C_c)*N*H)*dt #host can't exist without already being in the system!
    dM <- (v*(1-(u_m*z))*(C_c + (fun(u_m,R)*C_a))*H*M - l*M)*dt
    dN <- (v*(1-(u_n*z))*(C_c + (fun(u_n,R)*C_a))*H*N - l*N)*dt
    ur <- u_m*dt 
    
    
    H <- H + dH
    M <- M + dM
    N<- N + dN
    R<- R + dR
    delta <- N / (N+M)
   ur <- (u_m)*(1-delta)
  mutset4.1[[i,j]] <- ur
    
  
  }
 }
}
uptakerate <- mutset4.1
```

# Next let's see how the host is doing?
```{r}
mutset4.2 <- matrix(NaN,nrow = 20, ncol = 20, dimnames = list(seq(1/20, 1, 1/20), seq(1/20, 1, 1/20))) 
dt <- 0.01

for(i in 1:nrow(mutset4.2)){ 
u_m <-  as.numeric(rownames(mutset4.2)[i]) 
   
#Setting initial conditions (letting ecological dynamics play out)   
tset <- seq(from=0, to= 200, length.out = 10000)
H.simu1 <- NaN*tset; H.simu1[1] <- 1
M.simu1 <- NaN*tset; M.simu1[1] <- 1
R.simu1 <- NaN*tset; R.simu1[1] <- 10


for(k in 2:length(tset)){
    dt <- tset[k] - tset[k-1] 
    H <- H.simu1[k-1] 
    M <- M.simu1[k-1]
    R <- R.simu1[k-1]
  
    
    dR <- (D*(R_0 - R) + s*H/c - u_m*R*M + l_x*M*x(u_m, R,H))*dt
    dH <- (c*g*x(u_m, R, H)*H*M  - (s*H) - ((fun(u_m,R)*C_a) + C_c)*M*H  )*dt #host can't exist without already being in the system!
    dM <- (v*(1-(u_m*z))*(C_c + (fun(u_m,R)*C_a))*H*M - l*M)*dt
  
    H.simu1[k] <- H + dH
    M.simu1[k] <- M + dM
    R.simu1[k] <- R + dR
    
}
# Save end values(@equilibrium) to holding vector.
H0 <- H.simu1[length(tset)]
R0 <- R.simu1[length(tset)]
M_i <- M.simu1[length(tset)]

 H <- H0
 M <- M_i
 R <- R0

 dt <- 0.01
    
 for(j in 1: ncol(mutset4.2)){
    u_n <- as.numeric(colnames(mutset4.2)[j]) 
   
  delta <- 0.99
  numberofreps <- 0 

  # insert 1% of mutant population into the system
  N <- .01*M_i 
  M <- .99*M_i
  H <- H0
  R <- R0
 
  
  while(numberofreps < 1000000  && (delta < 0.995 && delta > 0.005)){
    numberofreps <- numberofreps + 1; 
    
     dR <- (D*(R_0 - R) + s*H/c - u_m*R*M + l_x*M*x(u_m, R, H) - u_n*R*N + l_y*N*x(u_n, R, H))*dt
    dH <- (c*g*x(u_m, R, H)*H*M + c*g*x(u_n, R, H)*H*N - (s*H) - ((fun(u_m,R)*C_a) + C_c)*M*H - ((fun(u_n,R)*C_a) + C_c)*N*H)*dt #host can't exist without already being in the system!
    dM <- (v*(1-(u_m*z))*(C_c + (fun(u_m,R)*C_a))*H*M - l*M)*dt
    dN <- (v*(1-(u_n*z))*(C_c + (fun(u_n,R)*C_a))*H*N - l*N)*dt
    
    H <- H + dH
    M <- M + dM
    N<- N + dN
    R<- R + dR
    mutset4.2[[i,j]] <- H  
  }
   } 
 
}
 
#Host_abundance4 <- mutset4.2
print(round(mutset4.2,3))
```

#Plot Host ab. vs resident uptake rate
```{r}
plot(x = mutset4.1, y = mutset4.2, las = , ylab ="Host biomass", xlab = "Average Resident Uptake Rate at each mutation round")
```

