---
title: "Satfunc5.0_fid3"
author: "Natalie Chong"
date: "12/6/2020"
output: html_document
---

# 12/06/2020 - Our most recent markdown! This markdown records yet another variation of a fidelity function, fidelity as just our temporary resource pool abundance instead of saturating to it.
```{r}
D <- 0.5 # Dilution Rate (Outflow)
R_0 <- 25 # Inflow Concentration (Nitrogen)
l <- 0.05 # fungal mortality
s <- 0.05 # senescence coefficient
c <- 0.7 # host's C:N Ratio
z <- 0.3 #cost of being a mutualist per unit of uptake rate* 
C_a <- 0.3 #Allocation Carbon
C_c <- 0.2 #Construction Carbon 
v <- 0.1  #Conversion efficiency, Host carbon to more symbionts
a <- 1.872335 # Resource's half-saturation constant.**This is k in equation!**
l_x <- 0.2 # loss back to R pool per unit of nutrient, let resident and mutant to have the same loss
l_y <- 0.2
g <- 0.8 #Tree's per capita growth rate
#b 
uset <- seq(0, 1, 1/1000)
uset2 <- seq(0, 1, 1/100)
```

# Fidelity function.
```{r}
fun4 <- function(b,u_m,R,H){b*(u_m*R)/(l_x + g*H)} # Records fidelity as a function that can be called later, makes it more convenient. 
```

# Temporary resource pool function.
```{r}
x <- function(u_m, R, H){(u_m*R)/(l_x + g*H)} 
```

# Made PIP code into a function. Refer to the code below for a cool trick to vary each slice of step in varying uptake rates just by changing value of *step* before running each chunk of code.
```{r}
pip <- function(b, step) {myseq <- seq(0, 1, step) # Makes pip a function! variables within it are listed to be b and step. stuff after open-currly brace names a new function myseq, and defines as a value that ranges from 0 to 1, by "step".
mutset5.1 <- matrix(NaN, nrow=length(myseq), ncol=length(myseq),dimnames=list(myseq, myseq)) # cool matrix function. STUDY THIS! note that myseq was stolen from some other anotation and might make some scientists mildly mad.
dt <- 0.01 # defined time steps as 1/100 each step.

for(i in 1:nrow(mutset5.1)){ #mutset5.1: records every individual who won. nrow here is analogous to "length" command in regular for loops.
u_m <-  as.numeric(rownames(mutset5.1)[i]) # at each row, place the corresponding numeric u_m value into the "u_m" notation in our equations.
   
#**    
tset <- seq(from=0, to= 500, length.out = 5*10000/3) # length.out here is a little trick that enables us to increase our total time steps but not let everything to go outta whack.
H.simu1 <- NaN*tset; H.simu1[1] <- 1 # create our holding vector, full of NaNs with the initial value of 1. Multiplied by tset because we want it to be the same length
M.simu1 <- NaN*tset; M.simu1[1] <- 1
R.simu1 <- NaN*tset; R.simu1[1] <- 10

for(k in 2:length(tset)){ # runs inner loop that runs ecological dynamics. 
    dt <- tset[k] - tset[k-1] # each time we do tset would be the later tset value minus the previous time step.
    H <- H.simu1[k-1] 
    M <- M.simu1[k-1]
    R <- R.simu1[k-1]
    
    dR <- (D*(R_0 - R) + s*H/c - u_m*R*M + l_x*M*x(u_m, R,H))*dt
    dH <- (c*g*x(u_m, R, H)*H*M  - (s*H) - ((fun4(b,u_m,R,H)*C_a) + C_c)*M*H  )*dt #host can't exist without already being in the system!
    dM <- (v*(1-(u_m*z))*(C_c + (fun4(b,u_m,R,H)*C_a))*H*M - l*M)*dt
    H.simu1[k] <- H + dH
    M.simu1[k] <- M + dM
    R.simu1[k] <- R + dR
    
} 
# run this intial condition loop in a seperate markdown to make sure that everything has equilibrated.
H0 <- H.simu1[length(tset)] # Save where our has equilibrated in our a new holding vector, to initiate dynamics when mutants are present.
R0 <- R.simu1[length(tset)]
M_i <- M.simu1[length(tset)]

#Store Resident equilibrium values.
 H <- H0
 R <- R0
 M <- M_i
 dt <- 0.01

# For every value of u_n.
 for(j in 1: ncol(mutset5.1)){
    u_n <- as.numeric(colnames(mutset5.1)[j])
 
  numberofreps <- 0 
  H <- H0
  R <- R0
  N <- .01*M_i
  M <- .99*M_i
  
 
  
    N.N <- (v*(1-(u_n*z))*(C_c + (fun4(b,u_n,R,H)*C_a))*H - l)*dt # N.N would be our invasion fitness. It is basically our change in mutant abundance with changing time, divided by how many mutants there are in the population.
    
    
 mutset5.1[[i,j]] <- N.N # save the value of N.N into our matrix, at each corresponding column/row.
   

    if(i == j){N.N <- 0} #We added this. Maybe considered cheating, this line makes the diagonal zero regardless of what our simulation says.
    if(N.N > 0){mutset5.1[[i,j]] <- TRUE} 
    if(N.N <= 0){mutset5.1[[i,j]] <- FALSE}

 }
  }
 return(mutset5.1) # remember to include this return command so that R knows what to print when you call this function!ß
}
```

# PIP when b = 0.2, plot generated is equivalent to mutset5.8 down below. Same end-products generated from a different pathway and this one here is generated by calling the function *pip* that we've previously written.
```{r}
b <- 0.2
pip_b_.2 <- pip(b, 1/40) # this is by 1/40 of a step, which means that there are 41 columns and rows in total. In other words, our values of u_m that ranges from 0 to 1 are sliced up into 41 pieces (because we're also including 0 that's where the extra 1 piece is from.)

library('plot.matrix')
  par(mar = c(4,4,4,4))
  plot(pip_b_.2, border= NA, fmt.key ="%.2f", xlab= "Mutant Uptake Rate, u_n", ylab = "Resident Uptake Rate, u_m", col = c('white','black') ) 
    
```


# Host, Resident symbiont, and resource bifurcation diagram function.
```{r}
host_uptake <- function(b,u_m, R, H, M){uset2 <- seq(0, 1, 1/100) #decrease last input to make graph smooth
Hset <- NaN*uset2
Rset <- NaN*uset2
Mset <- NaN*uset2

for(i in 1:length(uset2)){
  u_m <- as.numeric(uset2[i])
tset <- seq(from=0, to= 500, length.out = 5/3*10000) # make sure that the two tsets are the same. (bifurcation here, and pip's below)
H.simu1 <- NaN*tset; H.simu1[1] <- 1
M.simu1 <- NaN*tset; M.simu1[1] <- 1
R.simu1 <- NaN*tset; R.simu1[1] <- 10

for(k in 2:length(tset)){
    dt <- tset[k] - tset[k-1] 
    H <- H.simu1[k-1] 
    M <- M.simu1[k-1]
    R <- R.simu1[k-1]
  
    
    dR <- (D*(R_0 - R) + s*H/c - u_m*R*M + l_x*M*x(u_m, R,H))*dt
    dH <- (c*g*x(u_m, R, H)*M*H  - (s*H) - ((fun4(b,u_m,R,H)*C_a) + C_c)*M*H  )*dt #added H term in the positive portion of the equation, host can't exist without already being in the system!
    dM <- (v*(1-(u_m*z))*(C_c + (fun4(b,u_m,R,H)*C_a))*H*M - l*M)*dt
  
    
    H.simu1[k] <- H + dH
    M.simu1[k] <- M + dM
    R.simu1[k] <- R + dR
    
    }
Hset[i] <- H.simu1[length(tset)]
Mset[i] <- M.simu1[length(tset)]
Rset[i] <- R.simu1[length(tset)]

}
return(list(Hset=Hset, Rset = Rset, Mset = Mset)) # !!! remember to include RETURN...
}
```


# When b = 0.2
```{r}
b = 0.2
```

```{r}
mutset5.21 <- matrix(NaN,nrow = 21, ncol = 21, dimnames = list(seq(0, 1, 1/20), seq(0, 1, 1/20))) #name rows to be u_m ; cols to be u_n. made a matrix thingie yay

dt <- 0.01

for(i in 1:nrow(mutset5.21)){ #mutset5.21: records every individual who won. nrow here is analogous to "length" command.
u_m <-  as.numeric(rownames(mutset5.21)[i]) 
   
#**    
tset <- seq(from=0, to= 500, length.out = 5*10000/3)
H.simu1 <- NaN*tset; H.simu1[1] <- 1
M.simu1 <- NaN*tset; M.simu1[1] <- 1
R.simu1 <- NaN*tset; R.simu1[1] <- 10

for(k in 2:length(tset)){
    dt <- tset[k] - tset[k-1] 
    H <- H.simu1[k-1] 
    M <- M.simu1[k-1]
    R <- R.simu1[k-1]
    
    dR <- (D*(R_0 - R) + s*H/c - u_m*R*M + l_x*M*x(u_m, R,H))*dt
    dH <- (c*g*x(u_m, R, H)*H*M  - (s*H) - ((fun4(b,u_m,R,H)*C_a) + C_c)*M*H  )*dt #host can't exist without already being in the system!
    dM <- (v*(1-(u_m*z))*(C_c + (fun4(b,u_m,R,H)*C_a))*H*M - l*M)*dt
    H.simu1[k] <- H + dH
    M.simu1[k] <- M + dM
    R.simu1[k] <- R + dR
    
} 
# run this intial condition loop in a seperate markdown to make sure that everything has equilibrated.
H0 <- H.simu1[length(tset)]
R0 <- R.simu1[length(tset)]
M_i <- M.simu1[length(tset)]

#Store Resident equilibrium values.
 H <- H0
 R <- R0
 M <- M_i
 dt <- 0.01

# For every value of u_n, run this chuck and record our invasion fitness!
 for(j in 1: ncol(mutset5.21)){
    u_n <- as.numeric(colnames(mutset5.21)[j])
 
  numberofreps <- 0 
  H <- H0
  R <- R0
  N <- .01*M_i
  M <- .99*M_i
  
 
  
    N.N <- (v*(1-(u_n*z))*(C_c + (fun4(b,u_n,R,H)*C_a))*H - l)*dt
    
    
 mutset5.21[[i,j]] <- N.N
   

    if(i == j){N.N <- 0} #We added this. Maybe considered cheating.
    if(N.N > 0){mutset5.21[[i,j]] <- TRUE} 
    if(N.N <= 0){mutset5.21[[i,j]] <- FALSE}

 }
  }
 

 library('plot.matrix')
  par(mar = c(4,4,4,4))
  plot(mutset5.21, border= NA, fmt.key ="%.2f", xlab= "Mutant Uptake Rate, u_n", ylab = "Resident Uptake Rate, u_m", col = c('white','black') ) 
    
```

# mutset5.8
```{r}
mutset5.8 <- matrix(NaN,nrow = 41, ncol = 41, dimnames = list(seq(0, 1, 1/40), seq(0, 1, 1/40))) #name rows to be u_m ; cols to be u_n. made a matrix thingie yay

dt <- 0.01

for(i in 1:nrow(mutset5.8)){ #mutset5.8: records every individual who won. nrow here is analogous to "length" command.
u_m <-  as.numeric(rownames(mutset5.8)[i]) 
   
#**    
tset <- seq(from=0, to= 500, length.out = 5*10000/3)
H.simu1 <- NaN*tset; H.simu1[1] <- 1
M.simu1 <- NaN*tset; M.simu1[1] <- 1
R.simu1 <- NaN*tset; R.simu1[1] <- 10

for(k in 2:length(tset)){
    dt <- tset[k] - tset[k-1] 
    H <- H.simu1[k-1] 
    M <- M.simu1[k-1]
    R <- R.simu1[k-1]
    
    dR <- (D*(R_0 - R) + s*H/c - u_m*R*M + l_x*M*x(u_m, R,H))*dt
    dH <- (c*g*x(u_m, R, H)*H*M  - (s*H) - ((fun4(b,u_m,R,H)*C_a) + C_c)*M*H  )*dt #host can't exist without already being in the system!
    dM <- (v*(1-(u_m*z))*(C_c + (fun4(b,u_m,R,H)*C_a))*H*M - l*M)*dt
    H.simu1[k] <- H + dH
    M.simu1[k] <- M + dM
    R.simu1[k] <- R + dR
    
} 
# run this intial condition loop in a seperate markdown to make sure that everything has equilibrated.
H0 <- H.simu1[length(tset)]
R0 <- R.simu1[length(tset)]
M_i <- M.simu1[length(tset)]

#Store Resident equilibrium values.
 H <- H0
 R <- R0
 M <- M_i
 dt <- 0.01

# For every value of u_n.
 for(j in 1: ncol(mutset5.8)){
    u_n <- as.numeric(colnames(mutset5.8)[j])
 
  numberofreps <- 0 
  H <- H0
  R <- R0
  N <- .01*M_i
  M <- .99*M_i
  
 
  
    N.N <- (v*(1-(u_n*z))*(C_c + (fun4(b,u_n,R,H)*C_a))*H - l)*dt
    
    
 mutset5.8[[i,j]] <- N.N
   

    if(i == j){N.N <- 0} #We added this. Maybe considered cheating.
    if(N.N > 0){mutset5.8[[i,j]] <- TRUE} 
    if(N.N <= 0){mutset5.8[[i,j]] <- FALSE}

 }
  }
 

 library('plot.matrix')
  par(mar = c(4,4,4,4))
  plot(mutset5.8, border= NA, fmt.key ="%.2f", xlab= "Mutant Uptake Rate, u_n", ylab = "Resident Uptake Rate, u_m", col = c('white','black') ) 
    
```

#Host abundance as a function of uptake rate when b = .2
```{r}
equil1 <- host_uptake(u_m, R, H, M)
uset2 <- seq(0, 1, 1/100)
plot(x = uset2, y = equil1$Hset, lwd = 2, xlab = "Uptake Rate, u_m", ylab = "Host Abundance at equilibrium, H*", col = 'darkgreen') 
```

# Four panel plot for when b = 0.2
```{r}
b <- 0.2
Hset2 <- host_uptake(b, u_m, R, H, M)
uset2 <- seq(0, 1, 1/100)

par(mfrow=c(2,2), mar = c(5,5,1,1)) # mfrow= makes four panel plot, 2 rows and 2 columns. whee; mar = c(bottom, left, top, right ) margin lengths!!
plot(x = uset2, y = Hset2$Hset, lwd = 2, xlab = "Uptake Rate, u_m", ylab = "Host Abundance at \n equilibrium, H*", col = 'darkgreen') # \n=  new line here.
plot(x = uset2, y = Hset2$Mset, lwd = 2, xlab = "Uptake Rate, u_m", ylab = "Resident Abundance \n at equilibrium, M*", col = 'skyblue') 
plot(x = uset2, y = Hset2$Rset, lwd = 2, xlab = "Uptake Rate, u_m", ylab = "Resource Abundance \n at equilibrium, R*", col = 'maroon') 
par(mar = c(4,5,4,2))
plot(pip_b_.2, border= NA,  fmt.key ="%.2f", xlab= "Mutant Uptake Rate, u_n", ylab = "Resident Uptake Rate, u_m", col = c('white','black') ) 

```


# When b = 1
```{r}
b = 1
```


```{r}
mutset5.20 <- matrix(NaN,nrow = 41, ncol = 41, dimnames = list(seq(0, 1, 1/40), seq(0, 1, 1/40))) #name rows to be u_m ; cols to be u_n. made a matrix thingie yay CHANGE 20 -> 40 and see what happens!

dt <- 0.01

for(i in 1:nrow(mutset5.20)){ #mutset5.20: records every individual who won. nrow here is analogous to "length" command.
u_m <-  as.numeric(rownames(mutset5.20)[i]) 
   
#**    
tset <- seq(from=0, to= 500, length.out = 5*10000/3)
H.simu1 <- NaN*tset; H.simu1[1] <- 1
M.simu1 <- NaN*tset; M.simu1[1] <- 1
R.simu1 <- NaN*tset; R.simu1[1] <- 10

for(k in 2:length(tset)){
    dt <- tset[k] - tset[k-1] 
    H <- H.simu1[k-1] 
    M <- M.simu1[k-1]
    R <- R.simu1[k-1]
    
    dR <- (D*(R_0 - R) + s*H/c - u_m*R*M + l_x*M*x(u_m, R,H))*dt
    dH <- (c*g*x(u_m, R, H)*H*M  - (s*H) - ((fun4(b,u_m,R,H)*C_a) + C_c)*M*H  )*dt #host can't exist without already being in the system!
    dM <- (v*(1-(u_m*z))*(C_c + (fun4(b,u_m,R,H)*C_a))*H*M - l*M)*dt
    H.simu1[k] <- H + dH
    M.simu1[k] <- M + dM
    R.simu1[k] <- R + dR
    
} 
# run this intial condition loop in a seperate markdown to make sure that everything has equilibrated.
H0 <- H.simu1[length(tset)]
R0 <- R.simu1[length(tset)]
M_i <- M.simu1[length(tset)]

#Store Resident equilibrium values.
 H <- H0
 R <- R0
 M <- M_i
 dt <- 0.01

# For every value of u_n.
 for(j in 1: ncol(mutset5.20)){
    u_n <- as.numeric(colnames(mutset5.20)[j])
 
  numberofreps <- 0 
  H <- H0
  R <- R0
  N <- .01*M_i
  M <- .99*M_i
  
 
  
    N.N <- (v*(1-(u_n*z))*(C_c + (fun4(b,u_n,R,H)*C_a))*H - l)*dt
    
    
 mutset5.20[[i,j]] <- N.N
   

    if(i == j){N.N <- 0} #We added this. Maybe considered cheating.
    if(N.N > 0){mutset5.20[[i,j]] <- TRUE} 
    if(N.N <= 0){mutset5.20[[i,j]] <- FALSE}

 }
  }
 

 library('plot.matrix')
  par(mar = c(4,4,4,4))
  plot(mutset5.20, border= NA, fmt.key ="%.2f", xlab= "Mutant Uptake Rate, u_n", ylab = "Resident Uptake Rate, u_m", col = c('white','black') ) 
    
```

#Host abundance as a function of uptake rate when b = 1
```{r}
Hset1 <- host_uptake(b, u_m, R, H, M)
uset2 <- seq(0, 1, 1/100)

par(mfrow=c(2,2), mar = c(5,5,1,1)) # mfrow= makes four panel plot, 2 rows and 2 columns. whee; mar = c(bottom, left, top, right ) margin lengths!!
plot(x = uset2, y = Hset1$Hset, lwd = 2, xlab = "Uptake Rate, u_m", ylab = "Host Abundance at \n equilibrium, H*", col = 'darkgreen') # \n=  new like here.
plot(x = uset2, y = Hset1$Mset, lwd = 2, xlab = "Uptake Rate, u_m", ylab = "Resident Abundance \n at equilibrium, M*", col = 'skyblue') 
plot(x = uset2, y = Hset1$Rset, lwd = 2, xlab = "Uptake Rate, u_m", ylab = "Resource Abundance \n at equilibrium, R*", col = 'maroon') 
par(mar = c(4,7,4,2))
plot(mutset5.20, border= NA,  fmt.key ="%.2f", xlab= "Mutant Uptake Rate, u_n", ylab = "Resident Uptake Rate, u_m", col = c('white','black') ) 

```

#Resident symbiont Bifurcation diagram vs. u_m, when b = 1
```{r}
equil2 <- host_uptake(u_m, R, H, M)
uset2 <- seq(0, 1, 1/100)

plot(x = uset2, y = equil2$Mset, lwd = 2, xlab = "Uptake Rate, u_m", ylab = "Resident Abundance at equilibrium, M*", col = 'skyblue') # Dollar sign tells it to run a specific one of the saved equilbrias. 

```

