---
title: "Satfunc5.0_opt1"
author: "Natalie Chong"
date: "12/12/2020"
output: html_document
---

##### Modeling option 1, it is behaving weirdly. abandoned child.

### First and foremost, our parameter values have to be set to something.
```{r}
#b I have yet to define you.
#a <- 1.872335 # Resource's half-saturation constant.**This is k in equation!**
D <- 0.5 # Dilution Rate (Outflow)
R_0 <- 25 # Inflow Concentration (Nitrogen)
l <- 0.05 # fungal mortality
s <- 0.05 # senescence coefficient
c <- 0.7 # host's C:N Ratio
z <- 0.3 #cost of being a mutualist per unit of uptake rate* 
C_a <- 0.3 #Allocation Carbon
C_c <- 0.2 #Construction Carbon 
v <- 0.1  #Conversion efficiency, Host carbon to more symbionts
l_x <- 0.2 # loss back to R pool per unit of nutrient, let resident and mutant to have the same loss
l_y <- 0.2
g <- 0.8 #Tree's per capita growth rate
uset <- seq(0, 1, 1/1000)
uset2 <- seq(0, 1, 1/100)
```

### Fidelity function.
```{r}
fun4 <- function(b,u_m,R,M,H){b*(u_m*R*M)/(l_x + g*H)} # Fidelity is Xstar multiplied by a scaling 
```

### Temporary resource pool function.
```{r}
x <- function(u_m,R,M,H){(u_m*R*M)/(l_x + g*H)}
```

### PIP function.
```{r}
pip <- function(b, step) {myseq <- seq(0, 1, step) # Makes pip a function! variables within it are listed to be b and step. stuff after open-currly brace names a new function myseq, and defines as a value that ranges from 0 to 1, by "step".  Ignoring u_m = 0 here.
mutset5.1 <- matrix(NaN, nrow=length(myseq), ncol=length(myseq),dimnames=list(myseq, myseq)) # cool matrix function. STUDY THIS! note that myseq was stolen from some other annotation and might make some scientists mildly mad.
dt <- 0.01 # defined time steps as 1/100 each step.

for(i in 1:nrow(mutset5.1)){ #mutset5.1: records every individual who won. nrow here is analogous to "length" command in regular for loops.
u_m <-  as.numeric(rownames(mutset5.1)[i]) # at each row, place the corresponding numeric u_m value into the "u_m" notation in our equations.
   
#**    
tset <- seq(from=0, to= 500, length.out = 5*10000/3) # length.out here is a little trick that enables us to increase our total time steps but not let everything to go outta whack.
H.simu1 <- NaN*tset; H.simu1[1] <- 5 # create our holding vector, full of NaNs with the initial value of 1. Multiplied by tset because we want it to be the same length
M.simu1 <- NaN*tset; M.simu1[1] <- .001
R.simu1 <- NaN*tset; R.simu1[1] <- 10

for(k in 2:length(tset)){ # runs inner loop that runs ecological dynamics. 
    dt <- tset[k] - tset[k-1] # each time we do tset would be the later tset value minus the previous time step.
    H <- H.simu1[k-1] 
    M <- M.simu1[k-1]
    R <- R.simu1[k-1]
    
    dR <- (D*(R_0 - R) + s*H/c - u_m*R*M + l_x*x(u_m,R,M,H))*dt
    dH <- (c*g*x(u_m,R,M,H)*H  - (s*H) - ((fun4(b,u_m,R,M,H)*C_a) +(C_c*M*H)))*dt #host can't exist without already being in the system, why we needed an H in our typically positive term!
    dM <- (v*(1-(u_m*z))*ifelse(((fun4(b,u_m,R,M,H)*C_a) +(C_c*M*H)) >= H, H,((fun4(b,u_m,R,M,H)*C_a) +(C_c*M*H))) - l*M)*dt#assuming that mutant draws really little so it's fun4 is insignificant.
    H.simu1[k] <- ifelse(H +dH >=0, H + dH, 0)       #if the first is true do the second, if the first is false do third.prevents negative host growth #PUT IN FUNCTION
    M.simu1[k] <- M + dM
    R.simu1[k] <- R + dR
    
} 
# run this initial condition loop in a separate markdown to make sure that everything has equilibrated.
H0 <- H.simu1[length(tset)] # Save where our has equilibrated in our a new holding vector, to initiate dynamics when mutants are present.
R0 <- R.simu1[length(tset)]
M_i <- M.simu1[length(tset)]

#Store Resident equilibrium values.
 H <- H0
 R <- R0
 M <- M_i
 dt <- 0.01

 print(paste("u_m =", u_m)) #REMEMBER ME! cool way to print values at this stage!
 print(paste("H =",H))
# For every value of u_n.
 for(j in 1: ncol(mutset5.1)){
    u_n <- as.numeric(colnames(mutset5.1)[j])
 
  numberofreps <- 0 
  H <- H0
  R <- R0
  N <- .01*M_i
  M <- .99*M_i
  
 

    #N.N <- (v*(1-(u_n*z))*(C_c*H + ((fun4(b,u_n,R,N,H)*C_a/N))) - l)*dt # N.N would be our invasion fitness. It is basically our change in mutant abundance (dN) with changing time (dt), divided by how many mutants there are in the population.
    N.N <- (v*(1-(u_n*z))*ifelse((((fun4(b,u_m,R,M,H)*C_a) +(C_c*M*H))) >= H, 0,{print(H);((fun4(b,u_n,R,1,H)*C_a/1) +(C_c*H))}) - l) # host is paying an eligible payments to the symbionts, there is too little mutants for mutants to demand more than the host can pay. 1 put there in place of N, because the invasion fitness is (dN/dt)/N. dt is remove because we don't need it to forecast things.
    
    
 mutset5.1[[i,j]] <- N.N # save the value of N.N into our matrix, at each corresponding column/row.
   

    if(i == j){N.N <- 0} #We added this. Maybe considered cheating, this line makes the diagonal zero regardless of what our simulation says.
    if(N.N > 0){mutset5.1[[i,j]] <- TRUE} 
    if(N.N <= 0){mutset5.1[[i,j]] <- FALSE}

 }
  }
 return(mutset5.1) # remember to include this return command so that R knows what to print when you call this function!
}
```

### To prevent negative host biomass~!
#```{r}

    dHdt <- ifelse(H > 0, c*g*x(u_m,R,M,H)*H  - (s*H) - ((fun4(b,u_m,R,M,H)*C_a) +(C_c*M*H)), 0)
    
    H <- ifelse(H >=0, H +dHdt*dt, 0)
   
#```

### Host, Resident symbiont, and resource bifurcation diagram function. Make sure to change me after! (equations have to match pip)
```{r}
host_uptake <- function(b,u_m, R, H, M){uset2 <- seq(0, 1, 1/100) #decrease last input to make graph smooth
Hset <- NaN*uset2
Rset <- NaN*uset2
Mset <- NaN*uset2

for(i in 1:length(uset2)){
  u_m <- as.numeric(uset2[i])
tset <- seq(from=0, to= 500, length.out = 5/3*10000) # make sure that the two tsets are the same. (bifurcation here, and pip's below)
H.simu1 <- NaN*tset; H.simu1[1] <- 1
M.simu1 <- NaN*tset; M.simu1[1] <- 1
R.simu1 <- NaN*tset; R.simu1[1] <- 10

for(k in 2:length(tset)){
    dt <- tset[k] - tset[k-1] 
    H <- H.simu1[k-1] 
    M <- M.simu1[k-1]
    R <- R.simu1[k-1]
  
    
    dR <- (D*(R_0 - R) + s*H/c - u_m*R*M + l_x*x(u_m,R,M,H))*dt
    dH <- (c*g*x(u_m,R,M,H)*H  - (s*H) - ((fun4(b,u_m,R,M,H)*C_a) +(C_c*M*H)))*dt #added H term in the positive portion of the equation, host can't exist without already being in the system!
    dM <- (v*(1-(u_m*z))*ifelse(((fun4(b,u_m,R,M,H)*C_a) +(C_c*M*H)) >= H, H,((fun4(b,u_m,R,M,H)*C_a) +(C_c*M*H))) - l*M)*dt#assuming that mutant draws really little so it's fun4 is insignificant.
    H.simu1[k] <- ifelse(H +dH >=0, H + dH, 0)       #if the first is true do the second, if the first is false do third.prevents negative host growth #PUT IN FUNCTION
  
    
    H.simu1[k] <- H + dH
    M.simu1[k] <- M + dM
    R.simu1[k] <- R + dR
    
    }
Hset[i] <- H.simu1[length(tset)]
Mset[i] <- M.simu1[length(tset)]
Rset[i] <- R.simu1[length(tset)]

}
return(list(Hset=Hset, Rset = Rset, Mset = Mset)) # !!! remember to include RETURN...
}
```

## No. 1 Let's define the value of b first! b = 0.1
```{r}
b <- 0.1
```

### Next, we would be calling the *PIP function* to make our PIP!
```{r}
pip_0.1b <- pip(b, 1/10) # this is by 1/40 of a step, which means that there are 41 columns and rows in total. In other words, our values of u_m that ranges from 0 to 1 are sliced up into 41 pieces (because we're also including 0 that's where the extra 1 piece is from.)

library('plot.matrix')
  par(mar = c(4,4,4,4))
  plot(pip_0.1b, border= NA, fmt.key ="%.1f", xlab= "Mutant Uptake Rate, u_n", ylab = "Resident Uptake Rate, u_m", col = c('white','black') ) #plotted.
```

### Four panel plot for when b = 0.1
```{r}
Hset2 <- host_uptake(b, u_m, R, H, M)
uset2 <- seq(0, 1, 1/100)

par(mfrow=c(2,2), mar = c(5,5,1,1)) # mfrow= makes four panel plot, 2 rows and 2 columns. whee; mar = c(bottom, left, top, right ) margin lengths!!
plot(x = uset2, y = Hset2$Hset, lwd = 2, xlab = "Uptake Rate, u_m", ylab = "Host Abundance at \n equilibrium, H*", col = 'darkgreen') # \n=  new line here.
plot(x = uset2, y = Hset2$Mset, lwd = 2, xlab = "Uptake Rate, u_m", ylab = "Resident Abundance \n at equilibrium, M*", col = 'skyblue') 
plot(x = uset2, y = Hset2$Rset, lwd = 2, xlab = "Uptake Rate, u_m", ylab = "Resource Abundance \n at equilibrium, R*", col = 'maroon') 
par(mar = c(5,5,1,3))
plot(pip_0.1b, border= NA,  fmt.key ="%.2f", xlab= "Mutant Uptake Rate, u_n", ylab = "Resident Uptake Rate, u_m", col = c('white','black') ) 

```

## No. 2 Let's define the value of b first! b = 0.2
```{r}
b <- 0.2
```

### Next, we would be calling the *PIP function* to make our PIP!
```{r}
pip_0.2b <- pip(b, 1/40) # this is by 1/40 of a step, which means that there are 41 columns and rows in total. In other words, our values of u_m that ranges from 0 to 1 are sliced up into 41 pieces (because we're also including 0 that's where the extra 1 piece is from.)

library('plot.matrix')
  par(mar = c(4,4,4,4))
  plot(pip_0.2b, border= NA, fmt.key ="%.1f", xlab= "Mutant Uptake Rate, u_n", ylab = "Resident Uptake Rate, u_m", col = c('white','black') ) #plotted.
```

### Four panel plot for when b = 0.2
```{r}
b <- 0.2
Hset2 <- host_uptake(b, u_m, R, H, M)
uset2 <- seq(0, 1, 1/100)

par(mfrow=c(2,2), mar = c(5,5,1,1)) # mfrow= makes four panel plot, 2 rows and 2 columns. whee; mar = c(bottom, left, top, right ) margin lengths!!
plot(x = uset2, y = Hset2$Hset, lwd = 2, xlab = "Uptake Rate, u_m", ylab = "Host Abundance at \n equilibrium, H*", col = 'darkgreen') # \n=  new line here.
plot(x = uset2, y = Hset2$Mset, lwd = 2, xlab = "Uptake Rate, u_m", ylab = "Resident Abundance \n at equilibrium, M*", col = 'skyblue') 
plot(x = uset2, y = Hset2$Rset, lwd = 2, xlab = "Uptake Rate, u_m", ylab = "Resource Abundance \n at equilibrium, R*", col = 'maroon') 
par(mar = c(5,5,1,3))
plot(pip_0.2b, border= NA,  fmt.key ="%.2f", xlab= "Mutant Uptake Rate, u_n", ylab = "Resident Uptake Rate, u_m", col = c('white','black') ) 

```

## No. 3 Let's define the value of b first! b = 0.3
```{r}
b <- 0.3
```

### Next, we would be calling the *PIP function* to make our PIP!
```{r}
pip_0.3b <- pip(b, 1/40) # this is by 1/40 of a step, which means that there are 41 columns and rows in total. In other words, our values of u_m that ranges from 0 to 1 are sliced up into 41 pieces (because we're also including 0 that's where the extra 1 piece is from.)

library('plot.matrix')
  par(mar = c(4,4,4,4))
  plot(pip_0.3b, border= NA, fmt.key ="%.1f", xlab= "Mutant Uptake Rate, u_n", ylab = "Resident Uptake Rate, u_m", col = c('white','black') ) #plotted.
```

### Four panel plot for when b = 0.3
```{r}
b <- 0.3
Hset2 <- host_uptake(b, u_m, R, H, M)
uset2 <- seq(0, 1, 1/100)

par(mfrow=c(2,2), mar = c(5,5,1,1)) # mfrow= makes four panel plot, 2 rows and 2 columns. whee; mar = c(bottom, left, top, right ) margin lengths!!
plot(x = uset2, y = Hset2$Hset, lwd = 2, xlab = "Uptake Rate, u_m", ylab = "Host Abundance at \n equilibrium, H*", col = 'darkgreen') # \n=  new line here.
plot(x = uset2, y = Hset2$Mset, lwd = 2, xlab = "Uptake Rate, u_m", ylab = "Resident Abundance \n at equilibrium, M*", col = 'skyblue') 
plot(x = uset2, y = Hset2$Rset, lwd = 2, xlab = "Uptake Rate, u_m", ylab = "Resource Abundance \n at equilibrium, R*", col = 'maroon') 
par(mar = c(5,5,1,3))
plot(pip_0.3b, border= NA,  fmt.key ="%.2f", xlab= "Mutant Uptake Rate, u_n", ylab = "Resident Uptake Rate, u_m", col = c('white','black') ) 

```

## No. 4 Let's define the value of b first! b = 0.4
```{r}
b <- 0.4
```

### Next, we would be calling the *PIP function* to make our PIP!
```{r}
pip_0.4b <- pip(b, 1/40) # this is by 1/40 of a step, which means that there are 41 columns and rows in total. In other words, our values of u_m that ranges from 0 to 1 are sliced up into 41 pieces (because we're also including 0 that's where the extra 1 piece is from.)

library('plot.matrix')
  par(mar = c(4,4,4,4))
  plot(pip_0.4b, border= NA, fmt.key ="%.1f", xlab= "Mutant Uptake Rate, u_n", ylab = "Resident Uptake Rate, u_m", col = c('white','black') ) #plotted.
```

### Four panel plot for when b = 0.4
```{r}
b <- 0.4
Hset2 <- host_uptake(b, u_m, R, H, M)
uset2 <- seq(0, 1, 1/100)

par(mfrow=c(2,2), mar = c(5,5,1,1)) # mfrow= makes four panel plot, 2 rows and 2 columns. whee; mar = c(bottom, left, top, right ) margin lengths!!
plot(x = uset2, y = Hset2$Hset, lwd = 2, xlab = "Uptake Rate, u_m", ylab = "Host Abundance at \n equilibrium, H*", col = 'darkgreen') # \n=  new line here.
plot(x = uset2, y = Hset2$Mset, lwd = 2, xlab = "Uptake Rate, u_m", ylab = "Resident Abundance \n at equilibrium, M*", col = 'skyblue') 
plot(x = uset2, y = Hset2$Rset, lwd = 2, xlab = "Uptake Rate, u_m", ylab = "Resource Abundance \n at equilibrium, R*", col = 'maroon') 
par(mar = c(5,5,1,3))
plot(pip_0.4b, border= NA,  fmt.key ="%.2f", xlab= "Mutant Uptake Rate, u_n", ylab = "Resident Uptake Rate, u_m", col = c('white','black') ) 

```

## No. 5 Let's define the value of b first! b = 0.5
```{r}
b <- 0.5
```

### Next, we would be calling the *PIP function* to make our PIP!
```{r}
pip_0.5b <- pip(b, 1/40) # this is by 1/40 of a step, which means that there are 41 columns and rows in total. In other words, our values of u_m that ranges from 0 to 1 are sliced up into 41 pieces (because we're also including 0 that's where the extra 1 piece is from.)

library('plot.matrix')
  par(mar = c(4,4,4,4))
  plot(pip_0.5b, border= NA, fmt.key ="%.1f", xlab= "Mutant Uptake Rate, u_n", ylab = "Resident Uptake Rate, u_m", col = c('white','black') ) #plotted.
```

### Four panel plot for when b = 0.5
```{r}
b <- 0.5
Hset2 <- host_uptake(b, u_m, R, H, M)
uset2 <- seq(0, 1, 1/100)

par(mfrow=c(2,2), mar = c(5,5,1,1)) # mfrow= makes four panel plot, 2 rows and 2 columns. whee; mar = c(bottom, left, top, right ) margin lengths!!
plot(x = uset2, y = Hset2$Hset, lwd = 2, xlab = "Uptake Rate, u_m", ylab = "Host Abundance at \n equilibrium, H*", col = 'darkgreen') # \n=  new line here.
plot(x = uset2, y = Hset2$Mset, lwd = 2, xlab = "Uptake Rate, u_m", ylab = "Resident Abundance \n at equilibrium, M*", col = 'skyblue') 
plot(x = uset2, y = Hset2$Rset, lwd = 2, xlab = "Uptake Rate, u_m", ylab = "Resource Abundance \n at equilibrium, R*", col = 'maroon') 
par(mar = c(5,5,1,3))
plot(pip_0.5b, border= NA,  fmt.key ="%.2f", xlab= "Mutant Uptake Rate, u_n", ylab = "Resident Uptake Rate, u_m", col = c('white','black') ) 

```

## No. 6 Let's define the value of b first! b = 0.6
```{r}
b <- 0.6
```

### Next, we would be calling the *PIP function* to make our PIP!
```{r}
pip_0.6b <- pip(b, 1/40) # this is by 1/40 of a step, which means that there are 41 columns and rows in total. In other words, our values of u_m that ranges from 0 to 1 are sliced up into 41 pieces (because we're also including 0 that's where the extra 1 piece is from.)

library('plot.matrix')
  par(mar = c(4,4,4,4))
  plot(pip_0.6b, border= NA, fmt.key ="%.1f", xlab= "Mutant Uptake Rate, u_n", ylab = "Resident Uptake Rate, u_m", col = c('white','black') ) #plotted.
```

### Four panel plot for when b = 0.6
```{r}
b <- 0.6
Hset2 <- host_uptake(b, u_m, R, H, M)
uset2 <- seq(0, 1, 1/100)

par(mfrow=c(2,2), mar = c(5,5,1,1)) # mfrow= makes four panel plot, 2 rows and 2 columns. whee; mar = c(bottom, left, top, right ) margin lengths!!
plot(x = uset2, y = Hset2$Hset, lwd = 2, xlab = "Uptake Rate, u_m", ylab = "Host Abundance at \n equilibrium, H*", col = 'darkgreen') # \n=  new line here.
plot(x = uset2, y = Hset2$Mset, lwd = 2, xlab = "Uptake Rate, u_m", ylab = "Resident Abundance \n at equilibrium, M*", col = 'skyblue') 
plot(x = uset2, y = Hset2$Rset, lwd = 2, xlab = "Uptake Rate, u_m", ylab = "Resource Abundance \n at equilibrium, R*", col = 'maroon') 
par(mar = c(5,5,1,3))
plot(pip_0.6b, border= NA,  fmt.key ="%.2f", xlab= "Mutant Uptake Rate, u_n", ylab = "Resident Uptake Rate, u_m", col = c('white','black') ) 

```

## No. 7 Let's define the value of b first! b = 0.7
```{r}
b <- 0.7
```

### Next, we would be calling the *PIP function* to make our PIP!
```{r}
pip_0.7b <- pip(b, 1/40) # this is by 1/40 of a step, which means that there are 41 columns and rows in total. In other words, our values of u_m that ranges from 0 to 1 are sliced up into 41 pieces (because we're also including 0 that's where the extra 1 piece is from.)

library('plot.matrix')
  par(mar = c(4,4,4,4))
  plot(pip_0.7b, border= NA, fmt.key ="%.1f", xlab= "Mutant Uptake Rate, u_n", ylab = "Resident Uptake Rate, u_m", col = c('white','black') ) #plotted.
```

### Four panel plot for when b = 0.7
```{r}
b <- 0.7
Hset2 <- host_uptake(b, u_m, R, H, M)
uset2 <- seq(0, 1, 1/100)

par(mfrow=c(2,2), mar = c(5,5,1,1)) # mfrow= makes four panel plot, 2 rows and 2 columns. whee; mar = c(bottom, left, top, right ) margin lengths!!
plot(x = uset2, y = Hset2$Hset, lwd = 2, xlab = "Uptake Rate, u_m", ylab = "Host Abundance at \n equilibrium, H*", col = 'darkgreen') # \n=  new line here.
plot(x = uset2, y = Hset2$Mset, lwd = 2, xlab = "Uptake Rate, u_m", ylab = "Resident Abundance \n at equilibrium, M*", col = 'skyblue') 
plot(x = uset2, y = Hset2$Rset, lwd = 2, xlab = "Uptake Rate, u_m", ylab = "Resource Abundance \n at equilibrium, R*", col = 'maroon') 
par(mar = c(5,5,1,3))
plot(pip_0.7b, border= NA,  fmt.key ="%.2f", xlab= "Mutant Uptake Rate, u_n", ylab = "Resident Uptake Rate, u_m", col = c('white','black') ) 

```

## No. 8 Let's define the value of b first! b = 0.8
```{r}
b <- .81
```


### PIP function 2. 
#```{r}
step <- 1/40
myseq <- seq(0, 1, step) # Makes pip a function! variables within it are listed to be b and step. stuff after open-curly brace names a new function myseq, and defines as a value that ranges from 0 to 1, by "step".
mutset5.2 <- matrix(NaN, nrow=length(myseq), ncol=length(myseq),dimnames=list(myseq, myseq)) # cool matrix function. STUDY THIS! note that myseq was stolen from some other anotation and might make some scientists mildly mad.
dt <- 0.01 # defined time steps as 1/100 each step.

for(i in 1:nrow(mutset5.2)){ #mutset5.2: records every individual who won. nrow here is analogous to "length" command in regular for loops.
u_m <-  as.numeric(rownames(mutset5.2)[i]) # at each row, place the corresponding numeric u_m value into the "u_m" notation in our equations.
   
#**    
tset <- seq(from=0, to= 500, length.out = 5*10000/3) # length.out here is a little trick that enables us to increase our total time steps but not let everything to go outta whack.
H.simu1 <- NaN*tset; H.simu1[1] <- 1 # create our holding vector, full of NaNs with the initial value of 1. Multiplied by tset because we want it to be the same length
M.simu1 <- NaN*tset; M.simu1[1] <- 1
R.simu1 <- NaN*tset; R.simu1[1] <- 10

for(k in 2:length(tset)){ # runs inner loop that runs ecological dynamics. 
    dt <- tset[k] - tset[k-1] # each time we do tset would be the later tset value minus the previous time step.
   
    H <- H.simu1[k-1]
    M <- M.simu1[k-1]
    R <- R.simu1[k-1]
    
    dR <- (D*(R_0 - R) + s*H/c - u_m*R*M + l_x*x(u_m,R,M,H))*dt
    dH <- (c*g*x(u_m,R,M,H)*H  - (s*H) - ((fun4(b,u_m,R,M,H)*C_a) +(C_c*M*H)))*dt#host can't exist without already being in the system, why we needed an H in our typically positive term!
     dHdt <- ifelse(H > 0, c*g*x(u_m,R,M,H)*H  - (s*H) - ((fun4(b,u_m,R,M,H)*C_a) +(C_c*M*H)), 0)
    dM <- (v*(1-(u_m*z))*((fun4(b,u_m,R,M,H)*C_a) +(C_c*M*H)) - l*M)*dt
    
    H <- ifelse(H >=0, H + (dHdt*dt), 0)
    H.simu1[k] <- H + dH
    M.simu1[k] <- M + dM
    R.simu1[k] <- R + dR
    
} 
# run this initial condition loop in a separate markdown to make sure that everything has equilibrated.
H0 <- H.simu1[length(tset)] # Save where our has equilibrated in our a new holding vector, to initiate dynamics when mutants are present.
R0 <- R.simu1[length(tset)]
M_i <- M.simu1[length(tset)]

#Store Resident equilibrium values.
 H <- H0
 R <- R0
 M <- M_i
 dt <- 0.01

# For every value of u_n.
 for(j in 1: ncol(mutset5.2)){
    u_n <- as.numeric(colnames(mutset5.2)[j])
 
  numberofreps <- 0 
  H <- H0
  R <- R0
  N <- .01*M_i
  M <- .99*M_i
  
 
  
    N.N <- (v*(1-(u_n*z))*(C_c + (fun4(b,u_n,R,N,H)*C_a))*H - l)*dt # N.N would be our invasion fitness. It is basically our change in mutant abundance (dN) with changing time (dt), divided by how many mutants there are in the population.
    
    
 mutset5.2[[i,j]] <- N.N # save the value of N.N into our matrix, at each corresponding column/row.
   

    if(i == j){N.N <- 0} #We added this. Maybe considered cheating, this line makes the diagonal zero regardless of what our simulation says.
    if(N.N > 0){mutset5.2[[i,j]] <- TRUE} 
    if(N.N <= 0){mutset5.2[[i,j]] <- FALSE}

 }
  }
 return(mutset5.2) # remember to include this return command so that R knows what to print when you call this function!



#```
### Next, we would be calling the *PIP function* to make our PIP!
```{r}
pip_0.8b <- pip(b, 1/40) # this is by 1/40 of a step, which means that there are 41 columns and rows in total. In other words, our values of u_m that ranges from 0 to 1 are sliced up into 41 pieces (because we're also including 0 that's where the extra 1 piece is from.)

library('plot.matrix')
  par(mar = c(4,4,4,4))
  plot(pip_0.8b, border= NA, fmt.key ="%.1f", xlab= "Mutant Uptake Rate, u_n", ylab = "Resident Uptake Rate, u_m", col = c('white','black') ) #plotted.
```

### Four panel plot for when b = 0.8
```{r}
b <- 0.8
Hset2 <- host_uptake(b, u_m, R, H, M)
uset2 <- seq(0, 1, 1/100)

par(mfrow=c(2,2), mar = c(5,5,1,1)) # mfrow= makes four panel plot, 2 rows and 2 columns. whee; mar = c(bottom, left, top, right ) margin lengths!!
plot(x = uset2, y = Hset2$Hset, lwd = 2, xlab = "Uptake Rate, u_m", ylab = "Host Abundance at \n equilibrium, H*", col = 'darkgreen') # \n=  new line here.
plot(x = uset2, y = Hset2$Mset, lwd = 2, xlab = "Uptake Rate, u_m", ylab = "Resident Abundance \n at equilibrium, M*", col = 'skyblue') 
plot(x = uset2, y = Hset2$Rset, lwd = 2, xlab = "Uptake Rate, u_m", ylab = "Resource Abundance \n at equilibrium, R*", col = 'maroon') 
#par(mar = c(5,5,1,3))
#plot(pip_0.8b, border= NA,  fmt.key ="%.2f", xlab= "Mutant Uptake Rate, u_n", ylab = "Resident Uptake Rate, u_m", col = c('white','black') ) 

```

## No. 9 Let's define the value of b first! b = 0.9
```{r}
b <- 0.9
```

### Next, we would be calling the *PIP function* to make our PIP!
```{r}
pip_0.9b <- pip(b, 1/40) # this is by 1/40 of a step, which means that there are 41 columns and rows in total. In other words, our values of u_m that ranges from 0 to 1 are sliced up into 41 pieces (because we're also including 0 that's where the extra 1 piece is from.)

library('plot.matrix')
  par(mar = c(4,4,4,4))
  plot(pip_0.9b, border= NA, fmt.key ="%.1f", xlab= "Mutant Uptake Rate, u_n", ylab = "Resident Uptake Rate, u_m", col = c('white','black') ) #plotted.
```

### Four panel plot for when b = 0.9
```{r}
b <- 0.9
Hset2 <- host_uptake(b, u_m, R, H, M)
uset2 <- seq(0, 1, 1/100)

par(mfrow=c(2,2), mar = c(5,5,1,1)) # mfrow= makes four panel plot, 2 rows and 2 columns. whee; mar = c(bottom, left, top, right ) margin lengths!!
plot(x = uset2, y = Hset2$Hset, lwd = 2, xlab = "Uptake Rate, u_m", ylab = "Host Abundance at \n equilibrium, H*", col = 'darkgreen') # \n=  new line here.
plot(x = uset2, y = Hset2$Mset, lwd = 2, xlab = "Uptake Rate, u_m", ylab = "Resident Abundance \n at equilibrium, M*", col = 'skyblue') 
plot(x = uset2, y = Hset2$Rset, lwd = 2, xlab = "Uptake Rate, u_m", ylab = "Resource Abundance \n at equilibrium, R*", col = 'maroon') 
par(mar = c(5,5,1,3))
plot(pip_0.9b, border= NA,  fmt.key ="%.2f", xlab= "Mutant Uptake Rate, u_n", ylab = "Resident Uptake Rate, u_m", col = c('white','black') ) 

```

## No. 10 Let's define the value of b first! b = 1.0
```{r}
b <- 1.0
```

### Next, we would be calling the *PIP function* to make our PIP!
```{r}
pip_1.0b <- pip(b, 1/40) # this is by 1/40 of a step, which means that there are 41 columns and rows in total. In other words, our values of u_m that ranges from 0 to 1 are sliced up into 41 pieces (because we're also including 0 that's where the extra 1 piece is from.)

library('plot.matrix')
  par(mar = c(4,4,4,4))
  plot(pip_1.0b, border= NA, fmt.key ="%.1f", xlab= "Mutant Uptake Rate, u_n", ylab = "Resident Uptake Rate, u_m", col = c('white','black') ) #plotted.
```

### Four panel plot for when b = 1.0
```{r}
b <- 1.0
Hset2 <- host_uptake(b, u_m, R, H, M)
uset2 <- seq(0, 1, 1/100)

par(mfrow=c(2,2), mar = c(5,5,1,1)) # mfrow= makes four panel plot, 2 rows and 2 columns. whee; mar = c(bottom, left, top, right ) margin lengths!!
plot(x = uset2, y = Hset2$Hset, lwd = 2, xlab = "Uptake Rate, u_m", ylab = "Host Abundance at \n equilibrium, H*", col = 'darkgreen') # \n=  new line here.
plot(x = uset2, y = Hset2$Mset, lwd = 2, xlab = "Uptake Rate, u_m", ylab = "Resident Abundance \n at equilibrium, M*", col = 'skyblue') 
plot(x = uset2, y = Hset2$Rset, lwd = 2, xlab = "Uptake Rate, u_m", ylab = "Resource Abundance \n at equilibrium, R*", col = 'maroon') 
par(mar = c(5,5,1,3))
plot(pip_1.0b, border= NA,  fmt.key ="%.2f", xlab= "Mutant Uptake Rate, u_n", ylab = "Resident Uptake Rate, u_m", col = c('white','black') ) 

```
## Model Time series that contains conditional-(ifelse) statement.
```{r}
b <- .8
tset <- seq(from=0, to= 500, length.out = 5*10000/3) # length.out here is a little trick that enables us to increase our total time steps but not let everything to go outta whack.
H.simu1 <- NaN*tset; H.simu1[1] <- 1 # create our holding vector, full of NaNs with the initial value of 1. Multiplied by tset because we want it to be the same length
M.simu1 <- NaN*tset; M.simu1[1] <- 1
R.simu1 <- NaN*tset; R.simu1[1] <- 10

for(k in 2:length(tset)){ # runs inner loop that runs ecological dynamics. 
    dt <- tset[k] - tset[k-1] # each time we do tset would be the later tset value minus the previous time step.
   
    H <- H.simu1[k-1]
    M <- M.simu1[k-1]
    R <- R.simu1[k-1]
    
    dR <- (D*(R_0 - R) + s*H/c - u_m*R*M + l_x*x(u_m,R,M,H))*dt
    dH <- (c*g*x(u_m,R,M,H)*H  - (s*H) - ((fun4(b,u_m,R,M,H)*C_a) +(C_c*M*H)))*dt#host can't exist without already being in the system, why we needed an H in our typically positive term!
    # dHdt <- ifelse(H > 0, c*g*x(u_m,R,M,H)*H  - (s*H) - ((fun4(b,u_m,R,M,H)*C_a) +(C_c*M*H)), 0) 
   # dM <- (v*(1-(u_m*z))*((fun4(b,u_m,R,M,H)*C_a) +(C_c*M*H)) - l*M)*dt
    dM <- (v*(1-(u_m*z))*ifelse(((fun4(b,u_m,R,M,H)*C_a) +(C_c*M*H)) >= H, H,((fun4(b,u_m,R,M,H)*C_a) +(C_c*M*H))) - l*M)*dt #PUT IN FUNCTION
    
    H.simu1[k] <- ifelse(H +dH >=0, H + dH, 0) #if the first is true do the second, if the first is false do third.#PUT IN FUNCTION
    M.simu1[k] <- M + dM
    R.simu1[k] <- R + dR
    
} 
# run this initial condition loop in a separate markdown to make sure that everything has equilibrated.
#H0 <- H.simu1[length(tset)] # Save where our has equilibrated in our a new holding vector, to initiate dynamics when mutants are present.
#R0 <- R.simu1[length(tset)]
#M_i <- M.simu1[length(tset)]

plot(x = tset, y = H.simu1, col = 'green',type = 'l',xlab = 'Time', ylab = 'Species biomass/Resource Abundance', lwd=.2,las=1) 
#line(x = tset, y = R.simu1,type='l',las=1,lwd=5,ylab='Resource',xlab='Time',col='maroon')
lines(x = tset, y = M.simu1, col = 'skyblue', lwd=2) 
#lines(x = tset, y = N.simu1, col = Ncol, lwd=2) 
#legend(x = 150, y = 20, legend = c('Host','Mutualist M', 'Resource'), lwd=2, col = c('green', 'skyblue','maroon',))

```
#### Fin, now your final task is to put this on overleaf, along with the equations, and a brief explanation of what you did what b is, etc.
#### oh also this needs to be on github. Along with our updated fid3, because the previous fid3 was a mess.