---
title: "Var_5.0"
author: "Natalie Chong"
date: "8/9/2020"
output: html_document
---
# This Markdown records my newest variation of equations proposed by Alexandra!
#In this variation, instead of fidelity saturating to resources, it saturates to the amount of resources that is actually uptaken by our fungal partners, X^*.

# Here are our latest equations. WIP
# Before invasion (no mutant(N) population yet..)
$$
\begin{align}
\frac{dR}{dt} &= D ( R_0 - R ) + \frac{1}{c} s H - u_mRM + l_x \cdot \frac{u_mRM}{l_x + gH} \\ 
\newline
\frac{dH}{dt} &= cgH \cdot \frac{u_mRM}{l_x + gH} - s H - ( f_m C_a + C_c ) M H \\ 
\newline
\frac{dM}{dt} &= v ( 1 - zu_m )  ( f_m C_a + C_c ) M H - l M\\ 
\newline
\frac{dX}{dt} &= \frac{u_mR}{k_m + R} \cdot M - l_xx - \frac{u_mRM}{l_x + gH} = 0 \\
\newline
f_m &= \frac{u_m \cdot \frac{u_mR}{l_x + gH}}{k_m + \frac{u_mR}{l_x + gH}}
\end{align}

$$

# After adding mutant.
$$
\begin{align}

\newline
\frac{dR}{dt} &= D ( R_0 - R ) + \frac{1}{c} s H - u_mMR  - u_nNR + l_xM \cdot \frac{u_mR}{l_x + gH} + l_yN \cdot  \frac{u_nR}{l_y + gH}\\ 
\newline
\frac{dH}{dt} &= cgH \cdot \frac{u_mRM}{l_x + gH} + cgH \cdot \frac{u_nRN}{l_y + gH} - s H - ( f_m C_a + C_c ) M H - ( f_n C_a + C_c ) N H \\ 
\newline
\frac{dM}{dt} &= v ( 1 - zu_m )  ( f_m C_a + C_c ) M H - l M\\ 
\newline
\frac{dY}{dt} &= \frac{u_nR}{k_n + R} \cdot M - l_yy - \frac{u_nRM}{l_y + gH} = 0
\newline
\frac{dN}{dt} &= v ( 1 - zu_n )  ( f_n C_a + C_c ) N H - l N
\newline
f_n &= \frac{u_n \cdot \frac{u_nR}{l_x + gH}}{k_n + \frac{u_nR}{l_x + gH}} \\ f_m &= \frac{u_m \cdot \frac{u_mR}{l_x + gH}}{k_m + \frac{u_mR}{l_x + gH}} \\ 
\end{align}
$$

#First lets figure out what the new half-saturation constant is!
```{r}
D <- 0.5 # Dilution Rate (Outflow)
R_0 <- 25 # Inflow Concentration (Nitrogen)
l <- 0.05 # fungal mortality
s <- 0.05 # senescence coefficient
c <- 0.7 # host's C:N Ratio
z <- 0.3 #cost of being a mutualist per unit of uptake rate* 
C_a <- 0.3 #Allocation Carbon
C_c <- 0.2 #Construction Carbon 
v <- 0.1  #Conversion efficiency, Host carbon to more symbionts
a <- 1.872335 # Resource's half-saturation constant.**This is k in equation!**
l_x <- 0.2 # loss back to R pool per unit of nutrient, let resident and mutant to have the same loss
l_y <- 0.2
g <- 0.8 #Tree's per capita groth rate

fun2 <- function(u_m,R){(((u_m)*((u_m*R)/(l_x + g*H)))/((a)+((u_m*R)/(l_x + g*H))))}
x <- function(u_m, R, H){(u_m*R)/(l_x + g*H)}
```


# Plotting R* as a function of uptake rate
```{r}
uset <- seq(1/20, 1, 1/20)
Rset <- NaN*uset

for(i in 1:length(uset)){
  u_m <- as.numeric(uset[i])
tset <- seq(from=0, to= 300, length.out = 10000)
H.simu1 <- NaN*tset; H.simu1[1] <- 1
M.simu1 <- NaN*tset; M.simu1[1] <- 1
R.simu1 <- NaN*tset; R.simu1[1] <- 10

for(k in 2:length(tset)){
    dt <- tset[k] - tset[k-1] 
    H <- H.simu1[k-1] 
    M <- M.simu1[k-1]
    R <- R.simu1[k-1]
  
    
    dR <- (D*(R_0 - R) + s*H/c - u_m*R*M + l_x*M*x(u_m, R,H))*dt
    dH <- (c*g*x(u_m, R, H)*H*M  - (s*H) - ((fun2(u_m,R)*C_a) + C_c)*M*H  )*dt #added H term in the positive portion of the equation, host can't exist without already being in the system!
    dM <- (v*(1-(u_m*z))*(C_c + (fun2(u_m,R)*C_a))*H*M - l*M)*dt
  
    
    H.simu1[k] <- H + dH
    M.simu1[k] <- M + dM
    R.simu1[k] <- R + dR
    
}
Rset[i] <- R.simu1[length(tset)]

}

plot(uset, Rset, type='l', col = Rcol, lwd=2, xlab = "Uptake Rate, u_m", ylab = "Host Abundance at equilibrium, R*")

#u_m = 0.5, is where R = 1.872335! 
Rset[10]
```

# Thus, our Half-saturation constant is determined to be 1.872335.

# Next let's try creating a PIP for your new sets of equations!
```{r}
mutset5.0 <- matrix(NaN,nrow = 20, ncol = 20, dimnames = list(seq(1/20, 1, 1/20), seq(1/20, 1, 1/20))) 
dt <- 0.01

for(i in 1:nrow(mutset5.0)){ 
u_m <-  as.numeric(rownames(mutset5.0)[i]) 
   
#Setting initial conditions (letting ecological dynamics play out)   
tset <- seq(from=0, to= 200, length.out = 10000)
H.simu1 <- NaN*tset; H.simu1[1] <- 1
M.simu1 <- NaN*tset; M.simu1[1] <- 1
R.simu1 <- NaN*tset; R.simu1[1] <- 10


for(k in 2:length(tset)){
    dt <- tset[k] - tset[k-1] 
    H <- H.simu1[k-1] 
    M <- M.simu1[k-1]
    R <- R.simu1[k-1]
  
    
    dR <- (D*(R_0 - R) + s*H/c - u_m*R*M + l_x*M*x(u_m, R,H))*dt
    dH <- (c*g*x(u_m, R, H)*H*M  - (s*H) - ((fun2(u_m,R)*C_a) + C_c)*M*H  )*dt #host can't exist without already being in the system!
    dM <- (v*(1-(u_m*z))*(C_c + (fun2(u_m,R)*C_a))*H*M - l*M)*dt
  
    H.simu1[k] <- H + dH
    M.simu1[k] <- M + dM
    R.simu1[k] <- R + dR
    
}
# Save end values(@equilibrium) to holding vector.
H0 <- H.simu1[length(tset)]
R0 <- R.simu1[length(tset)]
M_i <- M.simu1[length(tset)]

 H <- H0
 M <- M_i
 R <- R0

 dt <- 0.01
    
 for(j in 1: ncol(mutset5.0)){
    u_n <- as.numeric(colnames(mutset5.0)[j]) 
   
  delta <- 0.99
  numberofreps <- 0 

  # insert 1% of mutant population into the system
  N <- .01*M_i 
  M <- .99*M_i
  H <- H0
  R <- R0
 
  
  while(numberofreps < 1000000  && (delta < 0.995 && delta > 0.005)){
    numberofreps <- numberofreps + 1; 
    
     dR <- (D*(R_0 - R) + s*H/c - u_m*R*M + l_x*M*x(u_m, R, H) - u_n*R*N + l_y*N*x(u_n, R, H))*dt
    dH <- (c*g*x(u_m, R, H)*H*M + c*g*x(u_n, R, H)*H*N - (s*H) - ((fun2(u_m,R)*C_a) + C_c)*M*H - ((fun2(u_n,R)*C_a) + C_c)*N*H)*dt #host can't exist without already being in the system!
    dM <- (v*(1-(u_m*z))*(C_c + (fun2(u_m,R)*C_a))*H*M - l*M)*dt
    dN <- (v*(1-(u_n*z))*(C_c + (fun2(u_n,R)*C_a))*H*N - l*N)*dt
    
    H <- H + dH
    M <- M + dM
    N<- N + dN
    R<- R + dR
    delta <- N / (N+M)
    if(is.na(delta)){print("delta is not a number"); print(N); print (M)}
if(is.na(numberofreps)){print("#ofreps is not a number")} 
  }
  
   mutset5.0[[i,j]] <- delta  
   
   
   if (delta >= 0.995){  mutset5.0[[i,j]] <- 1  }
   if(delta <= 0.005){mutset5.0[[i,j]] <- 0  }
   } 
 
}
 
  print(round(mutset5.0, 3))
  
   library('plot.matrix')
  Mutant_percentage5<-mutset5.0
 par(mar = c(4,4,4,4))
  plot(Mutant_percentage5, border= NA, fmt.key ="%.2f", breaks = c(-0.1,0.012,1),xlab= "Mutant Uptake Rate, u_n", ylab = "Resident Uptake Rate, u_m", col = c('white','black') ) 
```


```{r}
mutset5.1 <- matrix(NaN,nrow = 20, ncol = 20, dimnames = list(seq(1/20, 1, 1/20), seq(1/20, 1, 1/20))) #name rows to be u_m ; cols to be u_n. made a matrix thingie yay

dt <- 0.01

for(i in 1:nrow(mutset5.1)){ #mutset5.1: records every individual who won. nrow here is analogous to "length" command.
u_m <-  as.numeric(rownames(mutset5.1)[i]) 
   
#**    
tset <- seq(from=0, to= 300, length.out = 10000)
H.simu1 <- NaN*tset; H.simu1[1] <- 1
M.simu1 <- NaN*tset; M.simu1[1] <- 1
R.simu1 <- NaN*tset; R.simu1[1] <- 10

for(k in 2:length(tset)){
    dt <- tset[k] - tset[k-1] 
    H <- H.simu1[k-1] 
    M <- M.simu1[k-1]
    R <- R.simu1[k-1]
    
    dR <- (D*(R_0 - R) + s*H/c - u_m*R*M + l_x*M*x(u_m, R,H))*dt
    dH <- (c*g*x(u_m, R, H)*H*M  - (s*H) - ((fun2(u_m,R)*C_a) + C_c)*M*H  )*dt #host can't exist without already being in the system!
    dM <- (v*(1-(u_m*z))*(C_c + (fun2(u_m,R)*C_a))*H*M - l*M)*dt
    H.simu1[k] <- H + dH
    M.simu1[k] <- M + dM
    R.simu1[k] <- R + dR
    
} 
# run this intial condition loop in a seperate markdown to make sure that everything has equilibrated.
H0 <- H.simu1[length(tset)]
R0 <- R.simu1[length(tset)]
M_i <- M.simu1[length(tset)]

#Store Resident equilibrium values.
 H <- H0
 R <- R0
 M <- M_i
 dt <- 0.01

# For every value of u_n.
 for(j in 1: ncol(mutset5.1)){
    u_n <- as.numeric(colnames(mutset5.1)[j])
 
  numberofreps <- 0 
  H <- H0
  R <- R0
  N <- .01*M_i
  M <- .99*M_i
  
 
  while(numberofreps < 1000000){ 
    numberofreps <- numberofreps + 1; 
    
    dR <- (D*(R_0 - R) + s*H/c - u_m*R*M + l_x*M*x(u_m, R, H) - u_n*R*N + l_y*N*x(u_n, R, H))*dt
    dH <- (c*g*x(u_m, R, H)*H*M + c*g*x(u_n, R, H)*H*N - (s*H) - ((fun2(u_m,R)*C_a) + C_c)*M*H - ((fun2(u_n,R)*C_a) + C_c)*N*H)*dt #host can't exist without already being in the system!
    dM <- (v*(1-(u_m*z))*(C_c + (fun2(u_m,R)*C_a))*H*M - l*M)*dt
    dN <- (v*(1-(u_n*z))*(C_c + (fun2(u_n,R)*C_a))*H*N - l*N)*dt
    N.N <- (v*(1-(u_n*z))*(C_c + (fun2(u_n,R)*C_a))*H - l)*dt
    
    H <- H + dH
    M <- M + dM
    N <- N + dN
    R <- R + dR
   
if(is.na(numberofreps)){print("#ofreps is not a number")}
  }
 mutset5.1[[i,j]] <- N.N
   }

  
    if(N.N > 0){mutset5.1[[i,j]] <- 1} 
    if(N.N <= 0){mutset5.1[[i,j]] <- 0}
}
  
   

 library('plot.matrix')
  par(mar = c(4,4,4,4))
  plot(mutset5.1, border= NA,  fmt.cell='%.1f', fmt.key ="%.2f", breaks = c(-0.1,0,1),xlab= "Mutant Uptake Rate, u_n", ylab = "Resident Uptake Rate, u_m", col = c('white','black','black') ) 
    
    
```

# Now our Host Bifurcation Diagram is up! 
```{r}
uset <- seq(1/20, 1, 1/20)
Hset <- NaN*uset

for(i in 1:length(uset)){
  u_m <- as.numeric(uset[i])
tset <- seq(from=0, to= 500, length.out = 100000)
H.simu1 <- NaN*tset; H.simu1[1] <- 1
M.simu1 <- NaN*tset; M.simu1[1] <- 1
R.simu1 <- NaN*tset; R.simu1[1] <- 10

for(k in 2:length(tset)){
    dt <- tset[k] - tset[k-1] 
    H <- H.simu1[k-1] 
    M <- M.simu1[k-1]
    R <- R.simu1[k-1]
  
    
    dR <- (D*(R_0 - R) + s*H/c - u_m*R*M + l_x*M*x(u_m, R,H))*dt
    dH <- (c*g*x(u_m, R, H)*H*M  - (s*H) - ((fun2(u_m,R)*C_a) + C_c)*M*H  )*dt #added H term in the positive portion of the equation, host can't exist without already being in the system!
    dM <- (v*(1-(u_m*z))*(C_c + (fun2(u_m,R)*C_a))*H*M - l*M)*dt
  
    
    H.simu1[k] <- H + dH
    M.simu1[k] <- M + dM
    R.simu1[k] <- R + dR
    
}
Hset[i] <- H.simu1[length(tset)]

}

plot(uset, Hset, type='l', lwd=2, xlab = "Uptake Rate, u_m", ylab = "Host Abundance at equilibrium, H*", col = Hcol)
```