---
title: "Xstar_f_um"
author: "Natalie Chong"
date: "11/23/2020"
output: html_document
---

#This Markdown's Goal is to look at the relationship between fidelity, f, Our Temporary Resource Pool(Abundance), Xstar, and Resident Uptake Rate, u_m.
#Xstar is a temporary resource pool (units :amount of resources,(nitrogen, phosphorus, etc)), representing resources that has been transfered to our host, but hadn't been utilized by our host to make more biomass.
```{r}
D <- 0.5 # Dilution Rate (Outflow)
R_0 <- 25 # Inflow Concentration (Nitrogen)
l <- 0.05 # fungal mortality
s <- 0.05 # senescence coefficient
c <- 0.7 # host's C:N Ratio
z <- 0.3 #cost of being a mutualist per unit of uptake rate* 
C_a <- 0.3 #Allocation Carbon
C_c <- 0.2 #Construction Carbon 
v <- 0.1  #Conversion efficiency, Host carbon to more symbionts
a <- 1.872335 # Resource's half-saturation constant.**This is k in equation!**
l_x <- 0.2 # loss back to R pool per unit of nutrient, let resident and mutant to have the same loss
l_y <- 0.2
g <- 0.8 #Tree's per capita growth rate

fun2 <- function(u_m,R){(((u_m)*((u_m*R)/(l_x + g*H)))/((a)+((u_m*R)/(l_x + g*H))))} #This is the function for fidelity, where 
x <- function(u_m, R, H){(u_m*R)/(l_x + g*H)}
```



# Code below records Xstar.
```{r}
uset <- seq(0, 1, 1/1000)
mutset5.2 <- NaN*uset


for(j in 1: length(mutset5.2)){
    u_m <- as.numeric(uset[j])
 
tset <- seq(from=0, to= 100, length.out = 1000)
H.simu1 <- NaN*tset; H.simu1[1] <- 1
M.simu1 <- NaN*tset; M.simu1[1] <- 1
R.simu1 <- NaN*tset; R.simu1[1] <- 10

for(k in 2:length(tset)){
    dt <- tset[k] - tset[k-1] 
    H <- H.simu1[k-1] 
    M <- M.simu1[k-1]
    R <- R.simu1[k-1]
  
    
    dR <- (D*(R_0 - R) + s*H/c - u_m*R*M + l_x*M*x(u_m, R,H))*dt
    dH <- (c*g*x(u_m, R, H)*M*H  - (s*H) - ((fun2(u_m,R)*C_a) + C_c)*M*H  )*dt #added H term in the positive portion of the equation, host can't exist without already being in the system!
    dM <- (v*(1-(u_m*z))*(C_c + (fun2(u_m,R)*C_a))*H*M - l*M)*dt
  
    
    H.simu1[k] <- H + dH
    M.simu1[k] <- M + dM
    R.simu1[k] <- R + dR
    
      x_temp <- x(u_m, R, H)
      
      
}
   mutset5.2[j] <- x_temp
 
}
   
plot(uset, mutset5.2, lwd = 2, type ="l", xlab = "Resident Uptake, u_m", ylab = "Temporary Resource Pool, X*", col =Rcol) # Plots Xstar as a function of uptake rate.

uset[501]
mutset5.2[501]
```

# parameter a should've been 0.4953479.

# Code below records fidelity.
```{r}
uset <- seq(0, 1, 1/1000)
mutset5.3 <- NaN*uset


for(j in 1: length(mutset5.3)){
    u_m <- as.numeric(uset[j])
 
tset <- seq(from=0, to= 100, length.out = 1000)
H.simu1 <- NaN*tset; H.simu1[1] <- 1
M.simu1 <- NaN*tset; M.simu1[1] <- 1
R.simu1 <- NaN*tset; R.simu1[1] <- 10

for(k in 2:length(tset)){
    dt <- tset[k] - tset[k-1] 
    H <- H.simu1[k-1] 
    M <- M.simu1[k-1]
    R <- R.simu1[k-1]
  
    
    dR <- (D*(R_0 - R) + s*H/c - u_m*R*M + l_x*M*x(u_m, R,H))*dt
    dH <- (c*g*x(u_m, R, H)*M*H  - (s*H) - ((fun2(u_m,R)*C_a) + C_c)*M*H  )*dt #added H term in the positive portion of the equation, host can't exist without already being in the system!
    dM <- (v*(1-(u_m*z))*(C_c + (fun2(u_m,R)*C_a))*H*M - l*M)*dt
  
    
    H.simu1[k] <- H + dH
    M.simu1[k] <- M + dM
    R.simu1[k] <- R + dR
    
      fid <- fun2(u_m,R)
      
      
}
   mutset5.3[j] <- fid
 

}

plot(uset, mutset5.3, lwd = 2, type ="l", xlab = "Resident Uptake, u_m", ylab = "Host Fidelity, f", col = Hcol) # Plots fidelity as a function of uptake rate.
```


# Plotting Fidelity v.s. Xstar
```{r}
plot(x= mutset5.2, y= mutset5.3, xlab = 'Temporary Resource Pool, X*', ylab = 'Host fidelity, f', lwd=2)
```



